\documentclass[letterpaper, 10pt]{article}
\usepackage[left=0.75in, right=0.75in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{multicol}
\usepackage{qrcode}
\usepackage{pgf}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{\vspace{10px}\\Cambridge Events - 2024-11-30}
\lhead{}
\rfoot{\thepage}
\newcommand{\headline}[1]{\textbf{\Large #1}\vspace{0.5em}}
\newcommand{\subtitle}[1]{\textit{\large #1}\vspace{0.5em}}
\newcommand{\byline}[1]{\textit{\large #1}\vspace{0.5em}}
\newcommand{\articlecontent}[1]{\small #1\vspace{1em}}
\begin{document}
\thispagestyle{empty}
\begin{center}
\headline{Cambridge Events}
\byline{2024-11-30}
\end{center}
\hrulefill
\begin{multicols}{2}\headline{September 20, 2024}

\subtitle{Blithe Spirit by Noel Coward}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-09-20-1930-Blithe-Spirit-by-Noel-Coward}
\vspace{10px}

Cambridge Community Players present Blithe Spirit by Noel Coward.Performances are at the Cambridge Arts Theatre - 47 Water Street South, Cambridge, ONTickets:  Adults \$25 / Students \$20   @    www.cambridgecommunityplayers.comBring your SAGE!
}
\vspace{10px}

\headline{September 21, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806591}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806953}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807090}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Cambridge Farmers' Market}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-09-21-0700-Cambridge-Farmers-Market}
\vspace{10px}

The Cambridge Farmers' Market is open year round 7am-1pm.We have something for everyone! Hot-prepared foods, meats,seafood, cheese,chutneys, pies, confections, preserves and seasonal vegetables.
}
\vspace{10px}

\subtitle{Community Clean-Up}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-09-21-0930-Community-Clean-Up}
\vspace{10px}


}
\vspace{10px}

\subtitle{Waste Management Presentations - Doors Open Waterloo Region}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-09-21-1000-Waste-Management-Presentations-Doors-Open-Waterloo}
\vspace{10px}

Come to Ken Seiling Waterloo Region Museum for free during Doors Open Waterloo Region! Visit the exhibit on Waterloo Region's history and learn something new about the place we call home. Enjoy presentations from the Region of Waterloo's Waste Management department at 11 a.m. and 1 p.m. about the Region’s commitment to managing and reducing waste. Enter a draw to win one of two green bin prize packs! Challenge yourself with a recycling relay race at 12:00 p.m. and 2:00 p.m. Pre-registration is recommended for the Waste Management presentations, via Eventbrite.Register here!
}
\vspace{10px}

\subtitle{"Remembering the Flood of '74: Building the Living Levee" Walking Tour}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-09-21-1000-Remembering-the-Flood-of-74-Building-the-Living-Le}
\vspace{10px}

Culture Days: Remembering the Flood of '74: Building the Living Levee"Forever etched in the memories of long-time Cambridge residents is the Great Flood of ’74. On May 17th of that year, the spring melt and weeks of rainy weather had caused the water levels in the Grand River to rise to record levels; there was little that could be done as the water poured over the banks and into Cambridge, overwhelming Galt and communities further south. It was the worst flash flooding in twenty years, causing nearly \$34 million in damage. In the aftermath of that historic flood, and to reduce the risk of future flooding, the Cambridge Living Levee as constructed along the river to protect Galt’s historic downtown core.Plan to join McDougall Cottage staff for an enlightening Culture Days walk. We’ll travel the path of the levee to explore this excellent example of human adaptation to flooding hazards, and learn how the levee continues to preserve the community around us.These free walks will leave fro
}
\vspace{10px}

\subtitle{Introduction to Laser Cutting}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11423545}
\vspace{10px}

Interested in using a laser cutter but have no idea where to start?Learn the basics of 2D design using CorelDraw, specifically with the laser cutter in-mind. We will also teach you to draw vector lines, cut out shapes and letters, and saving the design. When finished, you will have the skills to make designs for cutting and engraving.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Maker Programs |TAGS: |Technology |Makerspace |DIY |Culture Days |
}
\vspace{10px}

\subtitle{Uptown Preston Con}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-09-21-1100-Uptown-Preston-Con}
\vspace{10px}


}
\vspace{10px}

\subtitle{Welcoming Week: Tree of Welcome Art Cart}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11817685}
\vspace{10px}

Extend a hand and celebrate Welcoming Week with us.Create a leaf for the Tree of Welcome. Pick a colour, trace your hand, and cut out the shape. Add a message of welcome and decorate your hand to add it to our tree. The Tree of Welcome will remain in the lobby until Thanksgiving weekend.About Welcoming WeekWelcoming Week is an annual opportunity to recognize and celebrate the people, places, and values that help everyone feel welcome and give them a sense of belonging in their local community. This year’s Welcoming Week takes place from September 13 to September 22. Waterloo Region’s Welcoming Week celebrations include community picnics, film screenings, tours, community art projects, information nights, and Canadian Citizenship Ceremonies. The week's goal is to build stronger neighbourhoods and kinder communities through welcoming acts.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so 
}
\vspace{10px}

\subtitle{Welcoming Week: Tour of Queen's Square}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11604981}
\vspace{10px}

New to Cambridge? Learn about what the public library has to offer.Time to meet your new best friend, your local public library! Tour the Queen's Square location of the Cambridge Public Library (formerly Idea Exchange) and learn about the amazing services and programs available.Bring your identification with your full name and proof of your current address to register for a free membership.About Welcoming WeekWelcoming Week is an annual opportunity to recognize and celebrate the people, places, and values that help everyone feel welcome and give them a sense of belonging in their local community. This year’s Welcoming Week takes place from September 13 to September 22. Waterloo Region’s Welcoming Week celebrations include community picnics, film screenings, tours, community art projects, information nights, and Canadian Citizenship Ceremonies. The week's goal is to build stronger neighbourhoods and kinder communities through welcoming acts.AccessibilityIf you require an accessibility a
}
\vspace{10px}

\subtitle{"Remembering the Flood of '74: Building the Living Levee" Walking Tour}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-09-21-1300-Remembering-the-Flood-of-74-Building-the-Living-Le}
\vspace{10px}

Culture Days: Remembering the Flood of '74: Building the Living Levee"Forever etched in the memories of long-time Cambridge residents is the Great Flood of ’74. On May 17th of that year, the spring melt and weeks of rainy weather had caused the water levels in the Grand River to rise to record levels; there was little that could be done as the water poured over the banks and into Cambridge, overwhelming Galt and communities further south. It was the worst flash flooding in twenty years, causing nearly \$34 million in damage. In the aftermath of that historic flood, and to reduce the risk of future flooding, the Cambridge Living Levee as constructed along the river to protect Galt’s historic downtown core.Plan to join McDougall Cottage staff for an enlightening Culture Days walk. We’ll travel the path of the levee to explore this excellent example of human adaptation to flooding hazards, and learn how the levee continues to preserve the community around us.These free walks will leave fro
}
\vspace{10px}

\subtitle{Blithe Spirit by Noel Coward}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-09-21-1400-Blithe-Spirit-by-Noel-Coward}
\vspace{10px}

Cambridge Community Players present Blithe Spirit by Noel Coward.Performances are at the Cambridge Arts Theatre - 47 Water Street South, Cambridge, ONTickets:  Adults \$25 / Students \$20   @    www.cambridgecommunityplayers.comBring your SAGE!
}
\vspace{10px}

\subtitle{Board Game Café}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11423633}
\vspace{10px}

A welcoming and friendly atmosphere to play one or more table games.Try a new game, play a classic, or bring one of your favourites with you. From strategy to silly fun, all interest levels are welcome.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Games |Gamer |Culture Days |Board Games |
}
\vspace{10px}

\subtitle{Practice Your English}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642139}
\vspace{10px}

Meet new friends, learn about your community, share your culture and customs, and practice your English.Join us for casual conversation and connection led by experienced and friendly Cambridge Public Library volunteers.These weekly sessions cover various topics featuring group activities and one-on-one or one-on-two practice in a fun and helpful environment.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Learn English |Language |ESL |Conversation |
}
\vspace{10px}

\subtitle{Welcoming Week: From Far Away  Film Screening}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11662693}
\vspace{10px}

Welcome to newcomer families!This short animation tells the story of Saoussan, a young girl struggling to adjust to life in Canada after being uprooted from her war-torn homeland. She has come to seek a quieter and safer life, although memories of war and death linger, memories that are awakened when the children at her new school prepare for a scary Halloween. From Far Away speaks to the power within us all to adapt like Saoussan and to welcome a newcomer.Waterloo Region Migration Film FestivalEach year the Immigration Partnership and its member organizations come together to share film in the Waterloo Region Migration Film Festival. The goal of this festival is to capture the promise and challenges of migration, celebrate the contributions that migrants make to their new communities, and to help our community better understand the challenges our newcomer neighbors overcome as they make our region our home.This year, the festival will take place in late summer. Our goal is to foster o
}
\vspace{10px}

\subtitle{Schneider Creek Porch Party}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-09-21-1400-Schneider-Creek-Porch-Party}
\vspace{10px}

Join us on Saturday, Sept. 21st from 2-6 p.m. for the 10th Annual Schneider Creek Porch Party. The SCPP is a FREE neighbourhood music festival in the Schneider Creek neighbourhood of downtown Kitchener. Don’t forget to stop by the headliner porch at Schneider Haus!”
}
\vspace{10px}

\subtitle{Tween D&D}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11423721}
\vspace{10px}

Learn to play Dungeons & Dragons, the world's most popular role-playing game.An introductory Dungeons & Dragons session designed for younger players. In the Peril in Pinebrook adventure, you will help return a newborn dragon to its mother’s lair. Learn about rolling dice, role-playing, casting spells, engaging in combat, and more.Character sheets and dice will be provided.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Tween |Gaming |Games |Culture Days |Board Games |
}
\vspace{10px}

\subtitle{Blithe Spirit by Noel Coward}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-09-21-1930-Blithe-Spirit-by-Noel-Coward}
\vspace{10px}

Cambridge Community Players present Blithe Spirit by Noel Coward.Performances are at the Cambridge Arts Theatre - 47 Water Street South, Cambridge, ONTickets:  Adults \$25 / Students \$20   @    www.cambridgecommunityplayers.comBring your SAGE!
}
\vspace{10px}

\headline{September 22, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806592}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806954}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807091}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Waterloo Region Kidney Walk – Together we are stronger than kidney disease!}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-09-22-0900-Waterloo-Region-Kidney-Walk-Together-we-are-strong}
\vspace{10px}

Kidney Walks are a province-wide movement to raise funds to better the lives of our loved ones affected by kidney disease. It’s a time to celebrate, make connections, remember, and support each other to demonstrate the strength of our kidney community.When you join the Kidney Walk, you’re joining thousands of Canadians who believe that we can make a difference.We hope you will join us at the Waterloo Region Kidney Walk on September 22, 2024 and be part of our kidney community.The Kidney Walk raises crucial funds to support kidney disease research, and programs and services designed to improve the lives of Canadians living with kidney disease and those who care for them.Register at www.kidneywalk.ca or call 226 338 6961
}
\vspace{10px}

\subtitle{Blithe Spirit by Noel Coward}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-09-22-1400-Blithe-Spirit-by-Noel-Coward}
\vspace{10px}

Cambridge Community Players present Blithe Spirit by Noel Coward.Performances are at the Cambridge Arts Theatre - 47 Water Street South, Cambridge, ONTickets:  Adults \$25 / Students \$20   @    www.cambridgecommunityplayers.comBring your SAGE!
}
\vspace{10px}

\subtitle{Mihko Kiskisiwin-Blood Memory}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11640758}
\vspace{10px}

Authors Shantell Powel, Bill Coates, Cynthia Missabie, and Hope Engel read and share from the new anthology Mihko Kiskisiwin.Thomas King said, “The truth about stories is… stories are all that we are.” Colonization has tried to erase and eradicate Indigenous narratives for centuries. Even mainstream literature features the same kinds of stories told by the same voices. It fails to recognize the diversity of voices across Turtle Island. Stories exist and persist in diverse and divergent forms.Mihko Kiskisiwin is collection of Indigenous North American voices, from incarcerated and diversified Indigenous community members, elders, and youth to people with disabilities and 2SLGBTQIA+ people. This anthology by the Indigenous Poets Society (Saskatchewan–Ontario) showcases spoken and written poetry, fiction, and creative non-fiction from emerging and established artists, writers, and performers.Testimony is at the heart of this collection. With vulnerability and urgency, these writers illumi
}
\vspace{10px}

\headline{September 23, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806593}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806955}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807092}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Totstime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642549}
\vspace{10px}

Dance, sing, rhyme, and craft with your tot.Enjoy stories, songs, and movement. An excellent program to meet other children and caregivers in your community.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Community Desk: Welcome YMCA Immigrant Services}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11502189}
\vspace{10px}

As a primary settlement agency in Cambridge, YMCA Immigrant Services acts as a “first stop” for newcomers.Through the YMCA Library Settlement Partnerships (LSP), our Settlement Workers are located within the libraries to continue to support newcomer and immigrant needs. Our Settlement Workers can provide support with citizenship, housing, education, English language assessments, connecting with community resources, and much more. Through our collaboration with Idea Exchange, together we are working to foster a smooth transition into the Cambridge community.The Library Settlement Partnership program is a partnership of Idea Exchange, the YMCA’s Immigrant Services Program, and Immigration, Refugees, and Citizenship Canada (IRCC).Services Offered·  Virtual settlement support to newcomers·  Information sessions relevant to newcomer needs in collaboration with Idea Exchange·  LSP staff provide orientation to library services and referrals·  Services available virtually, over the phone, and 
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605208}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{Music n' Motion}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11641661}
\vspace{10px}

A high-energy dance party where we will move our bodies and create musical-themed crafts.We will sing, dance, read a story, and then make an instrument using household objects.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Music |
}
\vspace{10px}

\subtitle{Shake, Rattle, and Read}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11647012}
\vspace{10px}

Come shake, rattle, and read with us!Explore fun, active, and hands-on activities with your little one.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby |Activities |
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605164}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{3rd Annual Golf Classic}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-09-23-1100-3rd-Annual-Golf-Classic}
\vspace{10px}

The Saint Luke's Place 3rd annual golf classic is coming Monday, September 23, to one of Canada's most historic clubs, Galt Country Club, along the Grand River.Join us for a full day of chipping, putting, and driving, all to benefit local healthcare.New features this year will make the experience even more fun for casual and serious golfers.There will be prizes and raffle items and a post-play dinner. A tax receipt is provided for a portion of your registration fee.
}
\vspace{10px}

\subtitle{Community Desk: Welcome Kinbridge!}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11634035}
\vspace{10px}

Are you a newcomer trying to get ready for the Canadian workforce? Kinbridge is here to help.Kinbridge's Newcomer Employment Outreach offers support with resume and cover letter writing, interview preparation, job search advice, and integrating into the Canadian workplace.Drop in or contact Lily Magnus to book an appointment for referrals to workshops and training.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |EVENT TYPE: |Programs + Workshops |TAGS: |Resume |Jobs |Interviews |Employment |Cover Letter |Community |Careers |
}
\vspace{10px}

\subtitle{Reading Buddies}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11646918}
\vspace{10px}

Kids practice their reading with a teenage buddy.This program is designed for children struggling to read at their grade level. Reading skills will be developed and practiced through fun and interactive literacy-based group games and activities. Children will also have the opportunity to read one-on-one with their teen volunteer buddy.Teens interested in becoming a Reading Buddy must complete our online volunteer application form. They will be contacted for an interview and orientation by our volunteer coordinator.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |
}
\vspace{10px}

\subtitle{Craft Stop}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11669921}
\vspace{10px}

Make a different craft each week.This social gathering is a fun way to show off your creative side and make something amazing.All materials provided.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Crafts |
}
\vspace{10px}

\subtitle{Photography for Beginners}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642224}
\vspace{10px}

Learn the basics of SLR-style photography.Learn the basics of SLR-style photography through the study of automatic and manual controls, focus, exposure, shutter speed, aperture, and flash work during this four-week course.Digital SLRs and mirrorless units are welcome.Please note there are no scheduled classes on October 14 and October 21.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Photography |Culture Days |CAGE |Art |
}
\vspace{10px}

\subtitle{Creative Oasis: Unplugged and Screen-Free}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11557458}
\vspace{10px}

Drop in and unplug: read, draw, colour, crochet, or do a puzzle in a relaxing atmosphere.Hang out in a relaxing room where you can read, draw, colour, crochet, knit, do a word or a jigsaw puzzle, or play a game of Chess.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Games |Activities |
}
\vspace{10px}

\headline{September 24, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806594}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806956}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807093}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Community Desk: Welcome YMCA Immigrant Services}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11502098}
\vspace{10px}

As a primary settlement agency in Cambridge, YMCA Immigrant Services acts as a “first stop” for newcomers.Through the YMCA Library Settlement Partnerships (LSP), our Settlement Workers are located within the libraries to continue to support newcomer and immigrant needs. Our Settlement Workers can provide support with citizenship, housing, education, English language assessments, connecting with community resources, and much more. Through our collaboration with Idea Exchange, together we are working to foster a smooth transition into the Cambridge community.The Library Settlement Partnership program is a partnership of Idea Exchange, the YMCA’s Immigrant Services Program, and Immigration, Refugees, and Citizenship Canada (IRCC).Services Offered·  Virtual settlement support to newcomers·  Information sessions relevant to newcomer needs in collaboration with Idea Exchange·  LSP staff provide orientation to library services and referrals·  Services available virtually, over the phone, and 
}
\vspace{10px}

\subtitle{Kindergarten Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11610617}
\vspace{10px}

Get ready for Kindergarten!Children will learn fundamental skills while having fun and meeting new friends.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |
}
\vspace{10px}

\subtitle{Stories and Stretches}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642602}
\vspace{10px}

Stretch it out and get your body moving.Come enjoy this unique program with its combination of stories, movement activities, and fun!AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |School Aged |Preschool |Activities |
}
\vspace{10px}

\subtitle{Preschool Picassos}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642483}
\vspace{10px}

Draw out your child's inner Picasso with amazing art projects.Each week, you and your child will use imagination and fun art supplies to explore and create. Please dress to get messy.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |Arts |
}
\vspace{10px}

\subtitle{STEAM Storytime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11666703}
\vspace{10px}

Twinkle, twinkle, little star, how I wonder what you are…Songs, rhymes, stories, and fun learning activities that inspire curious little minds to explore STEAM (science, technology, engineering, art, and math) and more.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |School Aged |Preschool |
}
\vspace{10px}

\subtitle{Baby Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498397}
\vspace{10px}

Get ready for some circle time fun!Learn new songs and rhymes, share stories, and meet other caregivers. At the same time, your little one will discover the exciting world around them. Baby Connections is a free community program that provides each family with a take-home kit of resources.Please only register once in your baby's first year.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Kindergarten Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11610686}
\vspace{10px}

Get ready for Kindergarten!Children will learn fundamental skills while having fun and meeting new friends.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Kindergarten |
}
\vspace{10px}

\subtitle{Art Through the Ages}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498234}
\vspace{10px}

Explore history from the 1920s-2020s through music, fashion, toys, and more.Together, we will make crafts, play games, and immerse ourselves in history.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Arts |
}
\vspace{10px}

\subtitle{Reading Buddies}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11646926}
\vspace{10px}

Kids practice their reading with a teenage buddy.This program is designed for children struggling to read at their grade level. Reading skills will be developed and practiced through fun and interactive literacy-based group games and activities. Children will also have the opportunity to read one-on-one with their teen volunteer buddy.Teens interested in becoming a Reading Buddy must complete our online volunteer application form. They will be contacted for an interview and orientation by our volunteer coordinator.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |
}
\vspace{10px}

\subtitle{Paws for Reading}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642192}
\vspace{10px}

Join our furry four-legged friends from Lions Club dog guides for the ultimate reading practice program.Children learn about service dogs from volunteers and then read to the doggies.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Animals |
}
\vspace{10px}

\subtitle{Recycle It!}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11666450}
\vspace{10px}

Discover the art of upcycling while turning your trash into treasure.This craft-based program will teach kids how to take everyday items and transform them in new and innovative ways.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Crafts |Arts |
}
\vspace{10px}

\subtitle{Galt Chess Club}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11799625}
\vspace{10px}

Fall adult drop-in chess club.Play the world's most popular board game with fellow chess enthusiasts. Boards and game pieces will be provided, but if you have your own set, you are welcome to bring it along.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Chess |Board Games |
}
\vspace{10px}

\subtitle{Remix: Sticker Art}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11666593}
\vspace{10px}

Make custom stickers!Make custom stickers using public domain books and original artwork. Learn about common image editing tools as you compose and print unique sticker pages.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |Maker Programs |TAGS: |Culture Days |Crafts |Crafting |Arts |
}
\vspace{10px}

\subtitle{Ukulele Meet-Up}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11424416}
\vspace{10px}

Enjoy singing and smiling while strumming your ukulele with this casual group.All skill levels are welcome. If needed, you can borrow a ukulele with your Idea Exchange membership.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Ukulele |Music |Meet-Up |Instruments |Culture Days |
}
\vspace{10px}

\subtitle{Practice Your English}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642119}
\vspace{10px}

Meet new friends, learn about your community, share your culture and customs, and practice your English.Join us for casual conversation and connection led by experienced and friendly Cambridge Public Library volunteers.These weekly sessions cover various topics featuring group activities and one-on-one or one-on-two practice in a fun and helpful environment.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Learn English |Language |ESL |Conversation |
}
\vspace{10px}

\subtitle{PJ Tales}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642448}
\vspace{10px}

Wear your pajamas and bring a stuffie to this evening storytime for families.Hear a bedtime story, sing songs, and make a craft to take home.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |School Aged |Preschool |
}
\vspace{10px}

\headline{September 25, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806595}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806957}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807094}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Totstime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642528}
\vspace{10px}

Dance, sing, rhyme, and craft with your tot.Enjoy stories, songs, and movement. An excellent program to meet other children and caregivers in your community.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Sensory Tales}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11646997}
\vspace{10px}

All the senses are celebrated in this inclusive sensory experience.Experience an immersive sensory story time filled with adventure.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Preschool |
}
\vspace{10px}

\subtitle{Hespeler Knitting Circle}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11424520}
\vspace{10px}

Share your ideas and creations with fellow knitters.Whether you’re an expert, or just starting out, everyone is welcome to participate, or just have some friendly conversation.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Programs + Workshops |Maker Programs |TAGS: |Knitting |Culture Days |Arts |
}
\vspace{10px}

\subtitle{Totstime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642512}
\vspace{10px}

Dance, sing, rhyme, and craft with your tot.Enjoy stories, songs, and movement. An excellent program to meet other children and caregivers in your community.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Baby Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498385}
\vspace{10px}

Get ready for some circle time fun!Learn new songs and rhymes, share stories, and meet other caregivers. At the same time, your little one will discover the exciting world around them. Baby Connections is a free community program that provides each family with a take-home kit of resources.Please only register once in your baby's first year.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605198}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605086}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{Connections 50+ Hespeler}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11425536}
\vspace{10px}

This older adult-focused program features a variety of entertaining activities such as local musicians, guest speakers, art activities, and much more.Writing instructor Larry Brown teaches how to start recording your memories.You've lived the adventures, now get them down on paper. Comb through the details of your life, small and large, and begin to map out your story. You will be surprised by how much you remember.About the InstructorLarry Brown has taught writing workshops throughout Ontario for over ten years. His stories have appeared in publications across Canada including The Fiddlehead, Prairie Fire, The Malahat Review, and internationally in Berlin’s SAND journal. His story “Triangle” appeared in Best Small Fictions 2017 and Oberon Press published his story collection TALK in 2009.Upcoming Connections 50+ Events at HespelerOctober 9: Music Trivia BingoOctober 23: Intro to Painting with VirginiaNovember 6: Generative Artificial Intelligence with guest speaker Amanda TkaczykNovem
}
\vspace{10px}

\subtitle{Maker Madness}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11641364}
\vspace{10px}

Enjoy this fun crafternoon with us while we make... anything!Try out some new skills with a different hands-on activity each week.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Activities |
}
\vspace{10px}

\subtitle{Afternoon Craft Club}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498156}
\vspace{10px}

Enjoy games, activities, crafts, and yummy snacks.Get crafty with a new project each week after school. Light refreshments will be provided.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Games |Crafts |
}
\vspace{10px}

\subtitle{Practice Your English}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642176}
\vspace{10px}

Meet new friends, learn about your community, share your culture and customs, and practice your English.Join us for casual conversation and connection led by experienced and friendly Cambridge Public Library volunteers.These weekly sessions cover various topics featuring group activities and one-on-one or one-on-two practice in a fun and helpful environment.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Learn English |Language |ESL |Conversation |
}
\vspace{10px}

\subtitle{Fibre Arts Meet-Up}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11447871}
\vspace{10px}

Join other fibre arts enthusiasts as you work on your own project in a social environment.Share ideas and tips with like-minded folks related to knit, crochet, embroidery, macrame, sewing, and other fibre arts for a weekly social meet-up.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |Maker Programs |TAGS: |Fibre |Culture Days |Crafts |Arts |
}
\vspace{10px}

\headline{September 26, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806596}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806958}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807095}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Community Desk: Welcome YMCA Immigrant Services}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11502123}
\vspace{10px}

As a primary settlement agency in Cambridge, YMCA Immigrant Services acts as a “first stop” for newcomers.Through the YMCA Library Settlement Partnerships (LSP), our Settlement Workers are located within the libraries to continue to support newcomer and immigrant needs. Our Settlement Workers can provide support with citizenship, housing, education, English language assessments, connecting with community resources, and much more. Through our collaboration with Idea Exchange, together we are working to foster a smooth transition into the Cambridge community.The Library Settlement Partnership program is a partnership of Idea Exchange, the YMCA’s Immigrant Services Program, and Immigration, Refugees, and Citizenship Canada (IRCC).Services Offered·  Virtual settlement support to newcomers·  Information sessions relevant to newcomer needs in collaboration with Idea Exchange·  LSP staff provide orientation to library services and referrals·  Services available virtually, over the phone, and 
}
\vspace{10px}

\subtitle{Totstime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642538}
\vspace{10px}

Dance, sing, rhyme, and craft with your tot.Enjoy stories, songs, and movement. An excellent program to meet other children and caregivers in your community.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{The Imagination Station}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11667656}
\vspace{10px}

Let your imagination run wild!From playing dress-up to flying in a make-believe airplane, children will have the opportunity to explore themselves and the world around them.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |
}
\vspace{10px}

\subtitle{Community Desk: Welcome WRSPC}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11639825}
\vspace{10px}

Learn about resources for how you can help yourself, someone else, and coping with suicide loss.The Waterloo Region Suicide Prevention Council is a community-based non-profit aiming to increase awareness of and engagement in suicide prevention within our community to ultimately reduce suicide and its impact. We do so through education, training, and community engagement initiatives utilizing suicide prevention and positive life promotion messaging.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Newcomers |Kids |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Men
}
\vspace{10px}

\subtitle{Stories and Stretches}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642580}
\vspace{10px}

Stretch it out and get your body moving.Come enjoy this unique program with its combination of stories, movement activities, and fun!AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |School Aged |Preschool |Activities |
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605153}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{Homeschool Makers}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11640494}
\vspace{10px}

An interactive opportunity to explore a wide range of maker equipment.From innovative technologies to traditional art forms, explore something new each week.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |Maker Programs |TAGS: |Technology |Arts |
}
\vspace{10px}

\subtitle{Homeschool Heroes}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11610722}
\vspace{10px}

Calling all heroes! This program teaches kids that empathy can make us all heroes.We will read stories, play games, and finish each week with a craft.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |Games |Crafts |
}
\vspace{10px}

\subtitle{Preschool Picassos}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642471}
\vspace{10px}

Draw out your child's inner Picasso with amazing art projects.Each week, you and your child will use imagination and fun art supplies to explore and create. Please dress to get messy.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |Arts |
}
\vspace{10px}

\subtitle{Practice Your English}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642162}
\vspace{10px}

Meet new friends, learn about your community, share your culture and customs, and practice your English.Join us for casual conversation and connection led by experienced and friendly Cambridge Public Library volunteers.These weekly sessions cover various topics featuring group activities and one-on-one or one-on-two practice in a fun and helpful environment.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Learn English |Language |ESL |Conversation |
}
\vspace{10px}

\subtitle{Families Under the Rainbow}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11635773}
\vspace{10px}

In collaboration with SPECTRUM Waterloo Region's Rainbow Community Space.Read along with stories, make crafts, and have fun playing together in a safe and supported environment for 2SLGBTQ+ youth, families, and allies.This program is generously funded by a grant from the Lyle S. Hallman foundation.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |SPECTRUM |Queer |Preschool |2SLGBTQIA+ |
}
\vspace{10px}

\subtitle{Main Street Music Series}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-09-26-1700-Main-Street-Music-Series}
\vspace{10px}


}
\vspace{10px}

\subtitle{Bad Sculpture Night}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11425677}
\vspace{10px}

Create a beautifully bad artwork, all fun and no pressure!Make a delightfully bad sculpture using a variety of fun materials. An example will be demonstrated but you can let your imagination run wild.Presented by CAGE:AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Cambridge Art Galleries |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Culture Days |Crafts |CAGE |Arts |
}
\vspace{10px}

\subtitle{NFB Movie Screening: Wilfred Buck (2024)}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11425992}
\vspace{10px}

View an award-winning cinematic feature film presented by the NFB at the Old Post Office.Director: Lisa Jackson2024 | 96 min English, CreeHe’s from the “fresh-out-of-the-bush, partly civilized, colonized, displaced people,” and he’s here to take us to the stars. Lisa Jackson’s portrait of Cree Elder Wilfred Buck moves between earth and sky, past and present, bringing to life ancient teachings of Indigenous astronomy and cosmology to tell a story that spans generations. Adapted from Buck’s rollicking memoir, I Have Lived Four Lives, the film weaves together stories from his life, including his harrowing young years of displacement and addiction. Seamlessly fusing present-day scenes with cinematic re-enactments and archival footage, this intimate yet expansive documentary takes us on an inspiring journey to the space beyond, and to the spaces between us all.This film contains coarse language, substance abuse, and mature themes.View excerpts of this award-winning film and find out more ab
}
\vspace{10px}

\subtitle{Ukulele Meet-Up}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11424371}
\vspace{10px}

Enjoy singing and smiling while strumming your ukulele with this casual group.All skill levels are welcome. If needed, you can borrow a ukulele with your membership.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Ukulele |Music |Meet-Up |Instruments |Culture Days |
}
\vspace{10px}

\subtitle{Crafty Kids}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11557296}
\vspace{10px}

Get crafty!Get inspired by a story and then explore your creativity with unique crafts and art projects each week.Materials will be provided.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Crafts |Crafting |Arts |
}
\vspace{10px}

\headline{September 27, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806597}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806959}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807096}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Connections 50+ Presents Cambridge Third Age Learning}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11426267}
\vspace{10px}

The story of Canadian Dr. Anne Innis Dagg from Toronto to South Africa is shared by Mary Dagg.Learn about the life of Anne Innis Dagg from growing up in Toronto, to studying giraffes in South Africa, facing sexual discrimination at the university level when she returned to Canada and then eventually getting the accolades that were due to her including the Order of Canada and a movie about her life.About the PresenterMary Dagg is Anne’s daughter and the Chief Executive Officer of the Anne Innis Dagg Foundation. She is a CPA (Chartered Professional Accountant) and worked as a Senior Director of Finance at a large Bay Street law firm. In 2020, she decided to leave the financial world and has dedicated herself to her mother and her mother’s work. She accompanied Anne on her trip back to Fleur De Lys in South Africa and has been by her side when Anne received the Order of Canada, her honorary doctorate at the University of Waterloo, and many screenings and special events for the award-winni
}
\vspace{10px}

\subtitle{Preston Book Club}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11426045}
\vspace{10px}

Love to discuss the nuances of a great book?Our Preston Book Club meets monthly to discuss a set title, share our thoughts, and learn more about the books we love.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Book Clubs |TAGS: |Culture Days |Community |
}
\vspace{10px}

\subtitle{Kindness Rocks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11640513}
\vspace{10px}

Sing, dance, and practice self-confidence.It's time to sing and dance together to celebrate kindness! This music-based program encourages self-confidence as your little one practices new skills.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Singing |Preschool |Music |Dancing |
}
\vspace{10px}

\subtitle{Community Desk: Welcome YMCA Immigrant Services}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11502149}
\vspace{10px}

As a primary settlement agency in Cambridge, YMCA Immigrant Services acts as a “first stop” for newcomers.Through the YMCA Library Settlement Partnerships (LSP), our Settlement Workers are located within the libraries to continue to support newcomer and immigrant needs. Our Settlement Workers can provide support with citizenship, housing, education, English language assessments, connecting with community resources, and much more. Through our collaboration with Cambridge Public Library (formerly Idea Exchange), together we are working to foster a smooth transition into the Cambridge community.The Library Settlement Partnership program is a partnership of Idea Exchange, the YMCA’s Immigrant Services Program, and Immigration, Refugees, and Citizenship Canada (IRCC).Services Offered·  Virtual settlement support to newcomers·  Information sessions relevant to newcomer needs in collaboration with Cambridge Public Library (formerly Idea Exchange)·  LSP staff provide orientation to library ser
}
\vspace{10px}

\subtitle{Baby Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498372}
\vspace{10px}

Get ready for some circle time fun!Learn new songs and rhymes, share stories, and meet other caregivers. At the same time, your little one will discover the exciting world around them. Baby Connections is a free community program that provides each family with a take-home kit of resources.Please only register once in your baby's first year.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Stories and Stretches}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642621}
\vspace{10px}

Stretch it out and get your body moving.Come enjoy this unique program with its combination of stories, movement activities, and fun!AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |School Aged |Preschool |Activities |
}
\vspace{10px}

\subtitle{Hespeler Village Market}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-09-27-1500-Hespeler-Village-Market}
\vspace{10px}

The Hespeler Village Market is an urban farmers' market that focuses on the importance of building community connections and supporting local businesses. Village Market vendors represent a diverse mix of local food, artisan crafts and information booths for charities, not-for-profits and community groups. We focus on integrating the entire community into our Friday night market.
}
\vspace{10px}

\headline{September 28, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806598}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806960}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807097}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Cambridge Farmers' Market}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-09-28-0700-Cambridge-Farmers-Market}
\vspace{10px}

The Cambridge Farmers' Market is open year round 7am-1pm.We have something for everyone! Hot-prepared foods, meats,seafood, cheese,chutneys, pies, confections, preserves and seasonal vegetables.
}
\vspace{10px}

\subtitle{Harvest Day}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11447584}
\vspace{10px}

Celebrate fall and the harvest season!Enjoy games, crafts, sensory activities, and fall-themed fun to celebrate our garden and the culmination of our One Seed One Community project. Idea Exchange is also partnering with the Cambridge Food Bank to put on a Fresh Food Drive, so feel free to bring any produce or non-perishables.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Kids |Adults |EVENT TYPE: |Special Events |TAGS: |Garden |Games |Culture Days |Crafts |Activities |
}
\vspace{10px}

\subtitle{Introduction to Large Format Printing}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11447656}
\vspace{10px}

Calling all photographers and designers.Get to know the 24" large format printer in our Makerspace. Learn to import your photos and designs, set up an artboard, and look at the many settings and paper types it offers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Maker Programs |TAGS: |Technology |Makerspace |Maker |Culture Days |
}
\vspace{10px}

\subtitle{Downtown Cambridge Vintage and Art Market}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-09-28-1100-Downtown-Cambridge-Vintage-and-Art-Market}
\vspace{10px}


}
\vspace{10px}

\subtitle{AI Encounters: Past, Present, and Future}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-09-28-1100-AI-Encounters-Past-Present-and-Future}
\vspace{10px}

A lot of us already use AI in our daily lives, but we don't realize it. Learn about the past, present, and future of AI with hands-on activities everyone can enjoy. Explore AI in pop culture, spot the AI-generated images, and discover the history of AI.Highlights of the Event:Join us at AI Encounters to be inspired, informed, and involved in the next frontier of technology! Whether you’re a tech enthusiast, a curious learner, or a future AI leader, there’s something for everyone.Let’s shape the future together—one AI encounter at a time!
}
\vspace{10px}

\subtitle{Region-cy Tea Party}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-09-28-1200-Region-cy-Tea-Party}
\vspace{10px}

Put on your finest dress and join us for an afternoon of tea and pleasant companyDearest Gentle Neighbor,Is there anything truly as wonderful as a well-made cup of tea? Perhaps a cup of tea with pleasant company!It is with the utmost excitement that I announce there is something afoot at Schneider Haus. The whole ton is cordially invited to an afternoon of tea, joyous conversation, and games at Schneider Haus. There are whispers of a tournament of Pall Mall, a challenge to design your own fetching hand fan at the modeste, and a stunning violin performance. The day promises to hold the attention of many among the ton, and this author is sure to be in attendance.Join us from 12:00 pm - 1:30 pm or 2:00 pm - 3:30 pmSpace is limited. Tickets must be purchased in advance for all those attending.
}
\vspace{10px}

\subtitle{“Along the Grand”: Photography Workshop and Walk with Jason Gennings}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-09-28-1300-Along-the-Grand-Photography-Workshop-and-Walk-with}
\vspace{10px}

Join us for an exciting and fun hands-on photography workshop "Along the Grand" at McDougall Cottage, led by photography instructor and photojournalist, Jason Gennings. This immersive experience kicks off with a brief lecture on composition techniques, setting the stage for a creative journey along the scenic Grand River.Participants will explore downtown Galt, where the natural beauty of the river meets the urban landscape. From flowing water to striking architecture, you'll discover how these elements come together to create compelling images that tell a story.Along the way, you can expect personalized guidance from Jason, who will be on hand to offer tips, answer questions, and inspire your photographic creativity. Whether you’re a seasoned photographer or just starting out, this is your chance to hone your skills in a supportive and engaging environment.And don’t forget—your photos might just be the perfect entry for the upcoming Grand Inspirations Art Contest https://www.engagewr.
}
\vspace{10px}

\subtitle{Practice Your English}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642140}
\vspace{10px}

Meet new friends, learn about your community, share your culture and customs, and practice your English.Join us for casual conversation and connection led by experienced and friendly Cambridge Public Library volunteers.These weekly sessions cover various topics featuring group activities and one-on-one or one-on-two practice in a fun and helpful environment.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Learn English |Language |ESL |Conversation |
}
\vspace{10px}

\subtitle{Region-cy Tea Party}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-09-28-1400-Region-cy-Tea-Party}
\vspace{10px}

Put on your finest dress and join us for an afternoon of tea and pleasant companyDearest Gentle Neighbor,Is there anything truly as wonderful as a well-made cup of tea? Perhaps a cup of tea with pleasant company!It is with the utmost excitement that I announce there is something afoot at Schneider Haus. The whole ton is cordially invited to an afternoon of tea, joyous conversation, and games at Schneider Haus. There are whispers of a tournament of Pall Mall, a challenge to design your own fetching hand fan at the modeste, and a stunning violin performance. The day promises to hold the attention of many among the ton, and this author is sure to be in attendance.Join us from 12:00 pm - 1:30 pm or 2:00 pm - 3:30 pmSpace is limited. Tickets must be purchased in advance for all those attending.
}
\vspace{10px}

\headline{September 29, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806599}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806961}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807098}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Flavours of Fall Tea by the Grand at McDougall Cottage}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-09-29-1100-Flavours-of-Fall-Tea-by-the-Grand-at-McDougall-Cot}
\vspace{10px}

Plan to join us for this special Tea by the Grand, that celebrates the fall flavours we love most (apple or pumpkin anyone?). We’ll be serving up some delicious seasonal treats alongside a couple of McDougall Tea classics and bottomless tea, of course!  Please note: If you have questions regarding dietary restrictions please contact us before purchase at mcdougall@regionofwaterloo.ca. Gluten-free options are only available at our specialty gluten-free teas. Check our website for upcoming dates or please email us.  To assist staff with event set-up: If the members of your party are purchasing tickets individually, rather than under one reservation please email us in advance of the tea, so we can be sure to seat all the members of your party together mcdougall@regionofwaterloo.ca  Children under the age of three do not require a ticket, however please let us know if they are attending so that we can account for that when planning our seating arrangements  Reservations are required and sp
}
\vspace{10px}

\subtitle{Galt Jazz - September 29 Show}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-09-29-1400-Galt-Jazz-September-29-Show}
\vspace{10px}

Ready for the BIG one? Galt Jazz presents its final FREE outdoor show of the season, a Latin Jazz Street Party on lower Main Street on Sunday, September 29 from 2 to 5 PM. Lots of patios and shops open. Bring your friends, parents, and kids! Lots for kids to do!…bring a chair, relax, enjoy!www.galtjazz.com
}
\vspace{10px}

\headline{September 30, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806600}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806746}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806962}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807099}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Totstime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642550}
\vspace{10px}

Dance, sing, rhyme, and craft with your tot.Enjoy stories, songs, and movement. An excellent program to meet other children and caregivers in your community.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Community Desk: Welcome YMCA Immigrant Services}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11502190}
\vspace{10px}

As a primary settlement agency in Cambridge, YMCA Immigrant Services acts as a “first stop” for newcomers.Through the YMCA Library Settlement Partnerships (LSP), our Settlement Workers are located within the libraries to continue to support newcomer and immigrant needs. Our Settlement Workers can provide support with citizenship, housing, education, English language assessments, connecting with community resources, and much more. Through our collaboration with Idea Exchange, together we are working to foster a smooth transition into the Cambridge community.The Library Settlement Partnership program is a partnership of Idea Exchange, the YMCA’s Immigrant Services Program, and Immigration, Refugees, and Citizenship Canada (IRCC).Services Offered·  Virtual settlement support to newcomers·  Information sessions relevant to newcomer needs in collaboration with Idea Exchange·  LSP staff provide orientation to library services and referrals·  Services available virtually, over the phone, and 
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605209}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{Music n' Motion}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11641662}
\vspace{10px}

A high-energy dance party where we will move our bodies and create musical-themed crafts.We will sing, dance, read a story, and then make an instrument using household objects.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Music |
}
\vspace{10px}

\subtitle{Shake, Rattle, and Read}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11647013}
\vspace{10px}

Come shake, rattle, and read with us!Explore fun, active, and hands-on activities with your little one.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby |Activities |
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605165}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{Art Cart: Orange Shirt Day}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11669713}
\vspace{10px}

Drop in to create a unique craft in honor of Orange Shirt Day.Use string and beads to make your own necklace, bracelet or keychain.Presented by CAGE:AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |Cambridge Art Galleries |EVENT TYPE: |Programs + Workshops |TAGS: |Crafts |CAGE |Arts |
}
\vspace{10px}

\subtitle{Community Desk: Welcome Kinbridge!}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11634036}
\vspace{10px}

Are you a newcomer trying to get ready for the Canadian workforce? Kinbridge is here to help.Kinbridge's Newcomer Employment Outreach offers support with resume and cover letter writing, interview preparation, job search advice, and integrating into the Canadian workplace.Drop in or contact Lily Magnus to book an appointment for referrals to workshops and training.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |EVENT TYPE: |Programs + Workshops |TAGS: |Resume |Jobs |Interviews |Employment |Cover Letter |Community |Careers |
}
\vspace{10px}

\subtitle{Reading Buddies}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11646919}
\vspace{10px}

Kids practice their reading with a teenage buddy.This program is designed for children struggling to read at their grade level. Reading skills will be developed and practiced through fun and interactive literacy-based group games and activities. Children will also have the opportunity to read one-on-one with their teen volunteer buddy.Teens interested in becoming a Reading Buddy must complete our online volunteer application form. They will be contacted for an interview and orientation by our volunteer coordinator.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |
}
\vspace{10px}

\subtitle{Craft Stop}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11669922}
\vspace{10px}

Make a different craft each week.This social gathering is a fun way to show off your creative side and make something amazing.All materials provided.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Crafts |
}
\vspace{10px}

\subtitle{Photography for Beginners}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642225}
\vspace{10px}

Learn the basics of SLR-style photography.Learn the basics of SLR-style photography through the study of automatic and manual controls, focus, exposure, shutter speed, aperture, and flash work during this four-week course.Digital SLRs and mirrorless units are welcome.Please note there are no scheduled classes on October 14 and October 21.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Photography |Culture Days |CAGE |Art |
}
\vspace{10px}

\subtitle{Creative Oasis: Unplugged and Screen-Free}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11557459}
\vspace{10px}

Drop in and unplug: read, draw, colour, crochet, or do a puzzle in a relaxing atmosphere.Hang out in a relaxing room where you can read, draw, colour, crochet, knit, do a word or a jigsaw puzzle, or play a game of Chess.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Games |Activities |
}
\vspace{10px}

\headline{October 01, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806601}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806747}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806963}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807100}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Community Desk: Welcome YMCA Immigrant Services}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11502099}
\vspace{10px}

As a primary settlement agency in Cambridge, YMCA Immigrant Services acts as a “first stop” for newcomers.Through the YMCA Library Settlement Partnerships (LSP), our Settlement Workers are located within the libraries to continue to support newcomer and immigrant needs. Our Settlement Workers can provide support with citizenship, housing, education, English language assessments, connecting with community resources, and much more. Through our collaboration with Idea Exchange, together we are working to foster a smooth transition into the Cambridge community.The Library Settlement Partnership program is a partnership of Idea Exchange, the YMCA’s Immigrant Services Program, and Immigration, Refugees, and Citizenship Canada (IRCC).Services Offered·  Virtual settlement support to newcomers·  Information sessions relevant to newcomer needs in collaboration with Idea Exchange·  LSP staff provide orientation to library services and referrals·  Services available virtually, over the phone, and 
}
\vspace{10px}

\subtitle{Kindergarten Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11610618}
\vspace{10px}

Get ready for Kindergarten!Children will learn fundamental skills while having fun and meeting new friends.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |
}
\vspace{10px}

\subtitle{Stories and Stretches}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642603}
\vspace{10px}

Stretch it out and get your body moving.Come enjoy this unique program with its combination of stories, movement activities, and fun!AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |School Aged |Preschool |Activities |
}
\vspace{10px}

\subtitle{Art Cart}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11447831}
\vspace{10px}

Drop in to create a unique craft!Colour a drawing, make a collage, build a sculpture! Try something new each time you visit the Cambridge Art Gallery Education Art Cart.Presented by CAGE:AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |Cambridge Art Galleries |EVENT TYPE: |Programs + Workshops |TAGS: |Culture Days |CAGE |Arts |
}
\vspace{10px}

\subtitle{Preschool Picassos}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642484}
\vspace{10px}

Draw out your child's inner Picasso with amazing art projects.Each week, you and your child will use imagination and fun art supplies to explore and create. Please dress to get messy.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |Arts |
}
\vspace{10px}

\subtitle{STEAM Storytime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11666704}
\vspace{10px}

Twinkle, twinkle, little star, how I wonder what you are…Songs, rhymes, stories, and fun learning activities that inspire curious little minds to explore STEAM (science, technology, engineering, art, and math) and more.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |School Aged |Preschool |
}
\vspace{10px}

\subtitle{Baby Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498400}
\vspace{10px}

Get ready for some circle time fun!Learn new songs and rhymes, share stories, and meet other caregivers. At the same time, your little one will discover the exciting world around them. Baby Connections is a free community program that provides each family with a take-home kit of resources.Please only register once in your baby's first year.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Kindergarten Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11610687}
\vspace{10px}

Get ready for Kindergarten!Children will learn fundamental skills while having fun and meeting new friends.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Kindergarten |
}
\vspace{10px}

\subtitle{Art Through the Ages}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498235}
\vspace{10px}

Explore history from the 1920s-2020s through music, fashion, toys, and more.Together, we will make crafts, play games, and immerse ourselves in history.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Arts |
}
\vspace{10px}

\subtitle{Reading Buddies}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11646927}
\vspace{10px}

Kids practice their reading with a teenage buddy.This program is designed for children struggling to read at their grade level. Reading skills will be developed and practiced through fun and interactive literacy-based group games and activities. Children will also have the opportunity to read one-on-one with their teen volunteer buddy.Teens interested in becoming a Reading Buddy must complete our online volunteer application form. They will be contacted for an interview and orientation by our volunteer coordinator.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |
}
\vspace{10px}

\subtitle{Recycle It!}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11666451}
\vspace{10px}

Discover the art of upcycling while turning your trash into treasure.This craft-based program will teach kids how to take everyday items and transform them in new and innovative ways.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Crafts |Arts |
}
\vspace{10px}

\subtitle{Galt Chess Club}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11799626}
\vspace{10px}

Fall adult drop-in chess club.Play the world's most popular board game with fellow chess enthusiasts. Boards and game pieces will be provided, but if you have your own set, you are welcome to bring it along.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Chess |Board Games |
}
\vspace{10px}

\subtitle{Learn Morse Code with Cambridge Amateur Radio}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11685675}
\vspace{10px}

Learn this well-known code used in amateur radio, aviation, and the military.Join members of the Cambridge Amateur Radio Club in an eight-week series of classes that will teach you to use Morse code and some of the history behind it.Morse code, or CW as known among amateur radio operators, is using a combination of short and long ‘beeps’ of a tone. The number and the combination of short and long ‘beeps’ will signify a letter. You will be surprised at how quickly you adapt to sense the difference among the various combinations and translate it to a letter, forming words and sentences. Learning Morse code is a great way to challenge your mind and keep it sharp.Amateur Radio (ham radio) is a popular hobby and service that brings people, electronics, and communication together. People use amateur radio to talk across town, around the world, or even into space, all without the Internet or cell phones. It's fun, social, educational, and can be a lifeline during times of need.This program ru
}
\vspace{10px}

\subtitle{Ukulele Meet-Up}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11424417}
\vspace{10px}

Enjoy singing and smiling while strumming your ukulele with this casual group.All skill levels are welcome. If needed, you can borrow a ukulele with your Idea Exchange membership.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Ukulele |Music |Meet-Up |Instruments |Culture Days |
}
\vspace{10px}

\subtitle{Employment Skill Building}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11558381}
\vspace{10px}

Join Starling Employment Services (formerly Lutherwood) for this free, open workshop series to build your job searching skills.Each session will provide information and practical tips on a different employment topic including goal setting, resumes, networking, interviews, and more. Choose a session that grabs your interest or join us for the entire series. We are looking forward to seeing you and giving you a taste of what Starling's Employment Services has to offer. Come take the next step of your job search journey with us. This week's topic is:Resume Foundations: It wouldn't be employment basics without talking about resumes! No nonsense information on what resumes are for, what they need, and how to get started writing them. If you have a resume, please bring it to edit in session.Tuesday, September 17: Job Search Preparation and Goal SettingTuesday, October 1: Resume FoundationsTuesday, October 15: Cover Letters and NetworkingTuesday, October 29: Interviewing with ConfidenceTuesda
}
\vspace{10px}

\subtitle{Practice Your English}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642120}
\vspace{10px}

Meet new friends, learn about your community, share your culture and customs, and practice your English.Join us for casual conversation and connection led by experienced and friendly Cambridge Public Library volunteers.These weekly sessions cover various topics featuring group activities and one-on-one or one-on-two practice in a fun and helpful environment.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Learn English |Language |ESL |Conversation |
}
\vspace{10px}

\subtitle{PJ Tales}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642449}
\vspace{10px}

Wear your pajamas and bring a stuffie to this evening storytime for families.Hear a bedtime story, sing songs, and make a craft to take home.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |School Aged |Preschool |
}
\vspace{10px}

\headline{October 02, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806602}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806748}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806964}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807101}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Totstime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642529}
\vspace{10px}

Dance, sing, rhyme, and craft with your tot.Enjoy stories, songs, and movement. An excellent program to meet other children and caregivers in your community.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Sensory Tales}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11646998}
\vspace{10px}

All the senses are celebrated in this inclusive sensory experience.Experience an immersive sensory story time filled with adventure.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Preschool |
}
\vspace{10px}

\subtitle{Hespeler Knitting Circle}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11424521}
\vspace{10px}

Share your ideas and creations with fellow knitters.Whether you’re an expert, or just starting out, everyone is welcome to participate, or just have some friendly conversation.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Programs + Workshops |Maker Programs |TAGS: |Knitting |Culture Days |Arts |
}
\vspace{10px}

\subtitle{Totstime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642514}
\vspace{10px}

Dance, sing, rhyme, and craft with your tot.Enjoy stories, songs, and movement. An excellent program to meet other children and caregivers in your community.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Baby Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498386}
\vspace{10px}

Get ready for some circle time fun!Learn new songs and rhymes, share stories, and meet other caregivers. At the same time, your little one will discover the exciting world around them. Baby Connections is a free community program that provides each family with a take-home kit of resources.Please only register once in your baby's first year.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605199}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605087}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{Lunch and Learn}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-10-02-1200-Lunch-and-Learn}
\vspace{10px}

NEW   Lunch and Learn Series  1 to 2 PMThe Ted Wake 50+ Centre invites you to a new series of Lunch and Learn events.September 10     Beer and Bangers                            Age Friendly ProgramsOctober  2           Lunch                                                    To Be AnnouncedFebruary 12        Homemade Soup tasting               To Be AnnouncedApril 15               Portuguese Shrimp Lunch              To Be AnnouncedPlease mark your calendars. More information will be provided.
}
\vspace{10px}

\subtitle{Maker Madness}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11641365}
\vspace{10px}

Enjoy this fun crafternoon with us while we make... anything!Try out some new skills with a different hands-on activity each week.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Activities |
}
\vspace{10px}

\subtitle{Afternoon Craft Club}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498157}
\vspace{10px}

Enjoy games, activities, crafts, and yummy snacks.Get crafty with a new project each week after school. Light refreshments will be provided.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Games |Crafts |
}
\vspace{10px}

\subtitle{Board Game Café}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11423639}
\vspace{10px}

From cards to Catan, this is a warm and friendly atmosphere for fans of low-tech table games.Try new games or bring your favourites with you. From deep strategy to goofy fun, all interest levels are welcome.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Games |Gamer |Culture Days |Board Games |
}
\vspace{10px}

\subtitle{Old Post Office Artists' Drawing Social}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11447861}
\vspace{10px}

Artists of all skill levels are invited to come out for some self-directed still life drawing practice.Each week there will be a different still life to draw from and an opportunity to meet and chat with other local artists.Bring any dry drawing supplies you'd like.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Cambridge Art Galleries |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Drawing |Culture Days |Arts |
}
\vspace{10px}

\subtitle{Practice Your English}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642177}
\vspace{10px}

Meet new friends, learn about your community, share your culture and customs, and practice your English.Join us for casual conversation and connection led by experienced and friendly Cambridge Public Library volunteers.These weekly sessions cover various topics featuring group activities and one-on-one or one-on-two practice in a fun and helpful environment.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Learn English |Language |ESL |Conversation |
}
\vspace{10px}

\subtitle{Fibre Arts Meet-Up}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11447872}
\vspace{10px}

Join other fibre arts enthusiasts as you work on your own project in a social environment.Share ideas and tips with like-minded folks related to knit, crochet, embroidery, macrame, sewing, and other fibre arts for a weekly social meet-up.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |Maker Programs |TAGS: |Fibre |Culture Days |Crafts |Arts |
}
\vspace{10px}

\subtitle{Cricut Basics}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11447902}
\vspace{10px}

Get started with the Cricut.Learn the essential first steps to using a Cricut machine and the Cricut Design Space software.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Maker Programs |TAGS: |Maker |Culture Days |Cricut |Crafting |
}
\vspace{10px}

\subtitle{Arctic Wildlife: Life on Svalbard}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11448028}
\vspace{10px}

View the beauty of the Norwegian Arctic Archipelago of Svalbard.The Norwegian arctic archipelago of Svalbard has more than 2,000 glaciers which provide habitat to hundreds of polar bears. In May, Paul Gains spent nine days aboard a Swedish coast guard vessel sailing around Svalbard’s sea ice looking for them.Now he would like to share this extraordinary experience with an audience.Life is harsh in the arctic and polar bears, walruses, and arctic foxes must adapt. Using dozens of photographs, Paul will tell tales of life above 78° North.Paul Gains has traveled the world writing about and photographing its wildlife. Now in his 30th year as a full time freelance journalist, he counts Svalbard as his most gratifying expedition.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10
}
\vspace{10px}

\subtitle{Queen's Square Book Club}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11448165}
\vspace{10px}

Read with us and have great discussions about amazing books.Read with us and have great discussions about amazing books.A traditional book club where we meet the first Wednesday night of every month. Great for people who work during the day but still want to enjoy a book club at night.Note: Books will be distributed at the previous meeting for the next meet up. If you were unable to attend would like a copy of the book, please ask at the Member Services desk at Queen’s Square.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Book Clubs |TAGS: |Culture Days |
}
\vspace{10px}

\headline{October 03, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806603}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806749}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806965}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807102}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Community Desk: Welcome YMCA Immigrant Services}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11502124}
\vspace{10px}

As a primary settlement agency in Cambridge, YMCA Immigrant Services acts as a “first stop” for newcomers.Through the YMCA Library Settlement Partnerships (LSP), our Settlement Workers are located within the libraries to continue to support newcomer and immigrant needs. Our Settlement Workers can provide support with citizenship, housing, education, English language assessments, connecting with community resources, and much more. Through our collaboration with Idea Exchange, together we are working to foster a smooth transition into the Cambridge community.The Library Settlement Partnership program is a partnership of Idea Exchange, the YMCA’s Immigrant Services Program, and Immigration, Refugees, and Citizenship Canada (IRCC).Services Offered·  Virtual settlement support to newcomers·  Information sessions relevant to newcomer needs in collaboration with Idea Exchange·  LSP staff provide orientation to library services and referrals·  Services available virtually, over the phone, and 
}
\vspace{10px}

\subtitle{Totstime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642539}
\vspace{10px}

Dance, sing, rhyme, and craft with your tot.Enjoy stories, songs, and movement. An excellent program to meet other children and caregivers in your community.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{The Imagination Station}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11667657}
\vspace{10px}

Let your imagination run wild!From playing dress-up to flying in a make-believe airplane, children will have the opportunity to explore themselves and the world around them.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |
}
\vspace{10px}

\subtitle{Stories and Stretches}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642581}
\vspace{10px}

Stretch it out and get your body moving.Come enjoy this unique program with its combination of stories, movement activities, and fun!AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |School Aged |Preschool |Activities |
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605154}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{Homeschool Makers}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11640495}
\vspace{10px}

An interactive opportunity to explore a wide range of maker equipment.From innovative technologies to traditional art forms, explore something new each week.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |Maker Programs |TAGS: |Technology |Arts |
}
\vspace{10px}

\subtitle{Homeschool Heroes}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11610723}
\vspace{10px}

Calling all heroes! This program teaches kids that empathy can make us all heroes.We will read stories, play games, and finish each week with a craft.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |Games |Crafts |
}
\vspace{10px}

\subtitle{Preschool Picassos}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642472}
\vspace{10px}

Draw out your child's inner Picasso with amazing art projects.Each week, you and your child will use imagination and fun art supplies to explore and create. Please dress to get messy.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |Arts |
}
\vspace{10px}

\subtitle{Practice Your English}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642163}
\vspace{10px}

Meet new friends, learn about your community, share your culture and customs, and practice your English.Join us for casual conversation and connection led by experienced and friendly Cambridge Public Library volunteers.These weekly sessions cover various topics featuring group activities and one-on-one or one-on-two practice in a fun and helpful environment.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Learn English |Language |ESL |Conversation |
}
\vspace{10px}

\subtitle{Families Under the Rainbow}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11635774}
\vspace{10px}

In collaboration with SPECTRUM Waterloo Region's Rainbow Community Space.Read along with stories, make crafts, and have fun playing together in a safe and supported environment for 2SLGBTQ+ youth, families, and allies.This program is generously funded by a grant from the Lyle S. Hallman foundation.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |SPECTRUM |Queer |Preschool |2SLGBTQIA+ |
}
\vspace{10px}

\subtitle{Main Street Music Series}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-10-03-1700-Main-Street-Music-Series}
\vspace{10px}


}
\vspace{10px}

\subtitle{SPECTRUM Cambridge Transgender Peer Support Group}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/10940717}
\vspace{10px}

Join SPECTRUM for a discussion and to meet other local gender-diverse folks.Funded by a grant from the Cambridge and North Dumfries Community Foundation, the biweekly Cambridge Transgender Peer Support Group is an informal, discussion-based, drop-in program. This group is a space for adults that identify within the trans/gender variant umbrella.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |SPECTRUM |Queer |Pride |2SLGBTQIA+ |
}
\vspace{10px}

\subtitle{Fairy-Lit Bottles}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11448296}
\vspace{10px}

An evening of painting upcycled glass bottles and listening to music in a relaxing atmosphere.An evening of glass bottle painting where we will use paints and various tools to create a unique art piece to light up the autumn nights. Examples will be provided for inspiration or you can design something unique.All materials will be provided to create a lit-up masterpiece.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Programs + Workshops |Maker Programs |TAGS: |Culture Days |Crafts |Crafting |
}
\vspace{10px}

\subtitle{Ukulele Meet-Up}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11424372}
\vspace{10px}

Enjoy singing and smiling while strumming your ukulele with this casual group.All skill levels are welcome. If needed, you can borrow a ukulele with your membership.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Ukulele |Music |Meet-Up |Instruments |Culture Days |
}
\vspace{10px}

\subtitle{Crafty Kids}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11557297}
\vspace{10px}

Get crafty!Get inspired by a story and then explore your creativity with unique crafts and art projects each week.Materials will be provided.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Crafts |Crafting |Arts |
}
\vspace{10px}

\subtitle{Bloody Berlin Walking Tour}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-10-03-1900-Bloody-Berlin-Walking-Tour}
\vspace{10px}

Join Schneider Haus staff for an evening walk through the back alleys and side streets of downtown Kitchener as we talk about some of the scary, sexy, or just plain weird characters that have called our town home. Murders, executions, grave robbing, shootouts, villainous doctors, and even pandemics of the past. Come learn a little more about Bloody Berlin….if you dare!Kick start your spooky season with us on Friday the 13th in September! There's no better time to learn about bloody Berlin than on the unluckiest day of the year!Admission:\$31 per person plus HST. Advance ticket purchase is required for this event, there will be no tickets sold at the door. Membership discount applies. No refunds.Information about Event:Suitable for ages 16 and up.Event runs rain or shine. This event takes place entirely outdoors and there will be no access to washrooms. The Historic Haus and galleries will be closed.Participants should dress for the weather and bring a flashlight (if possible).Please not
}
\vspace{10px}

\headline{October 04, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806604}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806750}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806966}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807103}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Kindness Rocks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11640514}
\vspace{10px}

Sing, dance, and practice self-confidence.It's time to sing and dance together to celebrate kindness! This music-based program encourages self-confidence as your little one practices new skills.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Singing |Preschool |Music |Dancing |
}
\vspace{10px}

\subtitle{Community Desk: Welcome YMCA Immigrant Services}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11502150}
\vspace{10px}

As a primary settlement agency in Cambridge, YMCA Immigrant Services acts as a “first stop” for newcomers.Through the YMCA Library Settlement Partnerships (LSP), our Settlement Workers are located within the libraries to continue to support newcomer and immigrant needs. Our Settlement Workers can provide support with citizenship, housing, education, English language assessments, connecting with community resources, and much more. Through our collaboration with Cambridge Public Library (formerly Idea Exchange), together we are working to foster a smooth transition into the Cambridge community.The Library Settlement Partnership program is a partnership of Idea Exchange, the YMCA’s Immigrant Services Program, and Immigration, Refugees, and Citizenship Canada (IRCC).Services Offered·  Virtual settlement support to newcomers·  Information sessions relevant to newcomer needs in collaboration with Cambridge Public Library (formerly Idea Exchange)·  LSP staff provide orientation to library ser
}
\vspace{10px}

\subtitle{Connections 50+ Queen's Square}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11692330}
\vspace{10px}

Connect with other adults while enjoying concerts, crafting, chats, and more.As part of our Connections 50+ suite of programming, this older adult-focused program features a variety of entertaining activities such as local musicians, guest speakers, art activities, and much more.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Seniors |Concert |Community |Arts |
}
\vspace{10px}

\subtitle{Baby Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498373}
\vspace{10px}

Get ready for some circle time fun!Learn new songs and rhymes, share stories, and meet other caregivers. At the same time, your little one will discover the exciting world around them. Baby Connections is a free community program that provides each family with a take-home kit of resources.Please only register once in your baby's first year.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Stories and Stretches}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642622}
\vspace{10px}

Stretch it out and get your body moving.Come enjoy this unique program with its combination of stories, movement activities, and fun!AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |School Aged |Preschool |Activities |
}
\vspace{10px}

\subtitle{Exhibition Celebration}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11271211}
\vspace{10px}

Celebrate the 20th Anniversary of FibreworksJoin us for a night of celebration! This year marks the 20th anniversary of Fibreworks, our biennial exhibition of fibre and textile-based works.Come and experience the work of 10 emerging artists working with fibre as a contemporary medium and hear about Fibreworks legacy during our panel talk with special guests: former Cambridge Art Galleries' Director and Fibreworks creator: Mary Misner; University of Waterloo Gallery Director/Curator and former Cambridge Art Galleries' Curator: Ivan Jurakic; and textile artist and past Fibreworks participant: Amanda McCavour.Light snacks and refreshments will be served. All are welcome to attend. Visit Next In Fibre at our Queen's Square Gallery and Fibreworks 20th Anniversary Collection Show at our Preston Gallery.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you req
}
\vspace{10px}

\subtitle{"The Dark Side of Galt" Evening Walking Tours}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-10-04-1830-The-Dark-Side-of-Galt-Evening-Walking-Tours}
\vspace{10px}

Put on your comfy walking shoes and join us as we take a summer stroll through the past, exploring stories of disasters, hauntings, murders and other unsavoury events that are part of the make up of Galt's dark history.Please note: Tours begin at 6:30 p.m. and 7:00 p.m. each night and run for approximately 90-minutes, departing from, and finishing up at McDougall Cottage.The tours may include hills, stairs and uneven terrain. Participants should dress for the weather. Phones are recommended, but not required, to access photos of the sites we are visiting. No washroom facilities available during tour.Ages 14 + only.October 18th Special Event - On October 18th there will be special tickets for any members of our walk who want to finish off the evening with a beverage and evening at Cafe 13 Food & Beverage. The special ticket price includes one 20oz beer, 6oz wine or feature cocktail, and cover waived (normal \$5) for the upstairs Taproom “Sisters of Salem” Dress Up Party featuring live mu
}
\vspace{10px}

\headline{October 05, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806605}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806751}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806967}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807104}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Cambridge Farmers' Market}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-10-05-0700-Cambridge-Farmers-Market}
\vspace{10px}

The Cambridge Farmers' Market is open year round 7am-1pm.We have something for everyone! Hot-prepared foods, meats,seafood, cheese,chutneys, pies, confections, preserves and seasonal vegetables.
}
\vspace{10px}

\subtitle{Islamic Heritage Month Display}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11866679}
\vspace{10px}

Join us and learn about our Muslim neighbors as they celebrate Islamic Heritage Month.It's Islamic Heritage Month in Canada, and we welcome the ICNA Sisters to Queen's Square to celebrate. Learn about the culture and heritage of our Islamic community members.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Special Events |TAGS: |Community |
}
\vspace{10px}

\subtitle{Introduction to Cricut Maker}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11448378}
\vspace{10px}

Learn the basics of our Cricut Maker.Learn to design a custom t-shirt or make beautiful cards and party decorations for any occasion with the Cricut Maker.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Maker Programs |TAGS: |Technology |Tech Training |Makerspace |Maker |Culture Days |Cricut |
}
\vspace{10px}

\subtitle{Ta'rikh: Islamic Cultural Heritage Celebration}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-10-05-1100-Tarikh-Islamic-Cultural-Heritage-Celebration}
\vspace{10px}

Celebrate Islamic History Month by attending Ta'rikh at Ken Seiling Waterloo Region Museum! - See historic Mecca, with a virtual reality tour by ISNA Canada (\$5 per viewing)- Explore local vendors and Islamic organizations- Henna artists- Face painting- Keynote address, spoken word, and oud performances from 3 p.m. - 4 p.m.FREE admissionVirtual reality tours of historic Mecca are \$5 per viewing
}
\vspace{10px}

\subtitle{Practice Your English}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642141}
\vspace{10px}

Meet new friends, learn about your community, share your culture and customs, and practice your English.Join us for casual conversation and connection led by experienced and friendly Cambridge Public Library volunteers.These weekly sessions cover various topics featuring group activities and one-on-one or one-on-two practice in a fun and helpful environment.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Learn English |Language |ESL |Conversation |
}
\vspace{10px}

\subtitle{Bloody Berlin Walking Tour}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-10-05-1900-Bloody-Berlin-Walking-Tour}
\vspace{10px}

Join Schneider Haus staff for an evening walk through the back alleys and side streets of downtown Kitchener as we talk about some of the scary, sexy, or just plain weird characters that have called our town home. Murders, executions, grave robbing, shootouts, villainous doctors, and even pandemics of the past. Come learn a little more about Bloody Berlin….if you dare!Kick start your spooky season with us on Friday the 13th in September! There's no better time to learn about bloody Berlin than on the unluckiest day of the year!Admission:\$31 per person plus HST. Advance ticket purchase is required for this event, there will be no tickets sold at the door. Membership discount applies. No refunds.Information about Event:Suitable for ages 16 and up.Event runs rain or shine. This event takes place entirely outdoors and there will be no access to washrooms. The Historic Haus and galleries will be closed.Participants should dress for the weather and bring a flashlight (if possible).Please not
}
\vspace{10px}

\headline{October 06, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806606}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806752}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806968}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807105}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\headline{October 07, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806607}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806753}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806969}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807106}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Totstime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642551}
\vspace{10px}

Dance, sing, rhyme, and craft with your tot.Enjoy stories, songs, and movement. An excellent program to meet other children and caregivers in your community.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Community Desk: Welcome YMCA Immigrant Services}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11502192}
\vspace{10px}

As a primary settlement agency in Cambridge, YMCA Immigrant Services acts as a “first stop” for newcomers.Through the YMCA Library Settlement Partnerships (LSP), our Settlement Workers are located within the libraries to continue to support newcomer and immigrant needs. Our Settlement Workers can provide support with citizenship, housing, education, English language assessments, connecting with community resources, and much more. Through our collaboration with Idea Exchange, together we are working to foster a smooth transition into the Cambridge community.The Library Settlement Partnership program is a partnership of Idea Exchange, the YMCA’s Immigrant Services Program, and Immigration, Refugees, and Citizenship Canada (IRCC).Services Offered·  Virtual settlement support to newcomers·  Information sessions relevant to newcomer needs in collaboration with Idea Exchange·  LSP staff provide orientation to library services and referrals·  Services available virtually, over the phone, and 
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605210}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{Music n' Motion}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11641663}
\vspace{10px}

A high-energy dance party where we will move our bodies and create musical-themed crafts.We will sing, dance, read a story, and then make an instrument using household objects.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Music |
}
\vspace{10px}

\subtitle{Shake, Rattle, and Read}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11647014}
\vspace{10px}

Come shake, rattle, and read with us!Explore fun, active, and hands-on activities with your little one.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby |Activities |
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605166}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{Community Desk: Welcome Kinbridge!}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11634037}
\vspace{10px}

Are you a newcomer trying to get ready for the Canadian workforce? Kinbridge is here to help.Kinbridge's Newcomer Employment Outreach offers support with resume and cover letter writing, interview preparation, job search advice, and integrating into the Canadian workplace.Drop in or contact Lily Magnus to book an appointment for referrals to workshops and training.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |EVENT TYPE: |Programs + Workshops |TAGS: |Resume |Jobs |Interviews |Employment |Cover Letter |Community |Careers |
}
\vspace{10px}

\subtitle{Reading Buddies}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11646920}
\vspace{10px}

Kids practice their reading with a teenage buddy.This program is designed for children struggling to read at their grade level. Reading skills will be developed and practiced through fun and interactive literacy-based group games and activities. Children will also have the opportunity to read one-on-one with their teen volunteer buddy.Teens interested in becoming a Reading Buddy must complete our online volunteer application form. They will be contacted for an interview and orientation by our volunteer coordinator.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |
}
\vspace{10px}

\subtitle{Craft Stop}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11669923}
\vspace{10px}

Make a different craft each week.This social gathering is a fun way to show off your creative side and make something amazing.All materials provided.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Crafts |
}
\vspace{10px}

\subtitle{Photography for Beginners}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642226}
\vspace{10px}

Learn the basics of SLR-style photography.Learn the basics of SLR-style photography through the study of automatic and manual controls, focus, exposure, shutter speed, aperture, and flash work during this four-week course.Digital SLRs and mirrorless units are welcome.Please note there are no scheduled classes on October 14 and October 21.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Photography |Culture Days |CAGE |Art |
}
\vspace{10px}

\subtitle{Creative Oasis: Unplugged and Screen-Free}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11557460}
\vspace{10px}

Drop in and unplug: read, draw, colour, crochet, or do a puzzle in a relaxing atmosphere.Hang out in a relaxing room where you can read, draw, colour, crochet, knit, do a word or a jigsaw puzzle, or play a game of Chess.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Games |Activities |
}
\vspace{10px}

\headline{October 08, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806608}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806754}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806970}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807107}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Community Desk: Welcome YMCA Immigrant Services}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11502100}
\vspace{10px}

As a primary settlement agency in Cambridge, YMCA Immigrant Services acts as a “first stop” for newcomers.Through the YMCA Library Settlement Partnerships (LSP), our Settlement Workers are located within the libraries to continue to support newcomer and immigrant needs. Our Settlement Workers can provide support with citizenship, housing, education, English language assessments, connecting with community resources, and much more. Through our collaboration with Idea Exchange, together we are working to foster a smooth transition into the Cambridge community.The Library Settlement Partnership program is a partnership of Idea Exchange, the YMCA’s Immigrant Services Program, and Immigration, Refugees, and Citizenship Canada (IRCC).Services Offered·  Virtual settlement support to newcomers·  Information sessions relevant to newcomer needs in collaboration with Idea Exchange·  LSP staff provide orientation to library services and referrals·  Services available virtually, over the phone, and 
}
\vspace{10px}

\subtitle{Kindergarten Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11610619}
\vspace{10px}

Get ready for Kindergarten!Children will learn fundamental skills while having fun and meeting new friends.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |
}
\vspace{10px}

\subtitle{Stories and Stretches}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642604}
\vspace{10px}

Stretch it out and get your body moving.Come enjoy this unique program with its combination of stories, movement activities, and fun!AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |School Aged |Preschool |Activities |
}
\vspace{10px}

\subtitle{Art Cart}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11447832}
\vspace{10px}

Drop in to create a unique craft!Colour a drawing, make a collage, build a sculpture! Try something new each time you visit the Cambridge Art Gallery Education Art Cart.Presented by CAGE:AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |Cambridge Art Galleries |EVENT TYPE: |Programs + Workshops |TAGS: |Culture Days |CAGE |Arts |
}
\vspace{10px}

\subtitle{Preschool Picassos}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642485}
\vspace{10px}

Draw out your child's inner Picasso with amazing art projects.Each week, you and your child will use imagination and fun art supplies to explore and create. Please dress to get messy.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |Arts |
}
\vspace{10px}

\subtitle{STEAM Storytime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11666705}
\vspace{10px}

Twinkle, twinkle, little star, how I wonder what you are…Songs, rhymes, stories, and fun learning activities that inspire curious little minds to explore STEAM (science, technology, engineering, art, and math) and more.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |School Aged |Preschool |
}
\vspace{10px}

\subtitle{Harvest Music Jam}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-10-08-1400-Harvest-Music-Jam}
\vspace{10px}

Tuesday October 8thHarvest Music JamOn Tuesday October 8th from 2:00 PM-4:00 PM, the Ted Wake 50+ Centre will be hosting Harvest Music Jam.  Enjoy a social afternoon with old and new friends. There will be  apples and pumpkins desserts, and you can sing your heart out with the Music Jam guitar players and musicians. Please register by Monday September 30th.Ted Wake Centre Fee: \$8.00                                                                                                        Activity  50608At the Johnson Centre – 31 Kribs StInfo: 519-740-4681 ext. 4460
}
\vspace{10px}

\subtitle{Baby Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498401}
\vspace{10px}

Get ready for some circle time fun!Learn new songs and rhymes, share stories, and meet other caregivers. At the same time, your little one will discover the exciting world around them. Baby Connections is a free community program that provides each family with a take-home kit of resources.Please only register once in your baby's first year.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Kindergarten Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11610688}
\vspace{10px}

Get ready for Kindergarten!Children will learn fundamental skills while having fun and meeting new friends.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Kindergarten |
}
\vspace{10px}

\subtitle{Art Through the Ages}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498236}
\vspace{10px}

Explore history from the 1920s-2020s through music, fashion, toys, and more.Together, we will make crafts, play games, and immerse ourselves in history.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Arts |
}
\vspace{10px}

\subtitle{Reading Buddies}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11646928}
\vspace{10px}

Kids practice their reading with a teenage buddy.This program is designed for children struggling to read at their grade level. Reading skills will be developed and practiced through fun and interactive literacy-based group games and activities. Children will also have the opportunity to read one-on-one with their teen volunteer buddy.Teens interested in becoming a Reading Buddy must complete our online volunteer application form. They will be contacted for an interview and orientation by our volunteer coordinator.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |
}
\vspace{10px}

\subtitle{Recycle It!}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11666452}
\vspace{10px}

Discover the art of upcycling while turning your trash into treasure.This craft-based program will teach kids how to take everyday items and transform them in new and innovative ways.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Crafts |Arts |
}
\vspace{10px}

\subtitle{Engineering Science Quest}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11609616}
\vspace{10px}

STEAM fun with our friends from the University of Waterloo.October 8: Ozocity builders: We will work together to design a living city using OzoBots. We’ll start by learning about the colour codes that OzoBots use to follow lines, speed up, or turn around. They’ll then draw their own section of a city on paper, coding instructions into the road. Everyone’s papers will then be combined to make a mega-city.October 29: Whimsical Webs: Mix digital design with real-life building, then sprinkle in some Augmented Reality to taste. What do you get? Your very own virtual spider pet!November 19: Scam Safety Hotline: Learn all about scam safety in a hotline-themed game show! We’ll first learn about common types of scams and how to identify them. Then, we’ll put our skills to the test by identifying scams and earning points for your team.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements
}
\vspace{10px}

\subtitle{Galt Chess Club}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11799627}
\vspace{10px}

Fall adult drop-in chess club.Play the world's most popular board game with fellow chess enthusiasts. Boards and game pieces will be provided, but if you have your own set, you are welcome to bring it along.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Chess |Board Games |
}
\vspace{10px}

\subtitle{Learn Morse Code with Cambridge Amateur Radio}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11685676}
\vspace{10px}

Learn this well-known code used in amateur radio, aviation, and the military.Join members of the Cambridge Amateur Radio Club in an eight-week series of classes that will teach you to use Morse code and some of the history behind it.Morse code, or CW as known among amateur radio operators, is using a combination of short and long ‘beeps’ of a tone. The number and the combination of short and long ‘beeps’ will signify a letter. You will be surprised at how quickly you adapt to sense the difference among the various combinations and translate it to a letter, forming words and sentences. Learning Morse code is a great way to challenge your mind and keep it sharp.Amateur Radio (ham radio) is a popular hobby and service that brings people, electronics, and communication together. People use amateur radio to talk across town, around the world, or even into space, all without the Internet or cell phones. It's fun, social, educational, and can be a lifeline during times of need.This program ru
}
\vspace{10px}

\subtitle{Ukulele Meet-Up}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11424418}
\vspace{10px}

Enjoy singing and smiling while strumming your ukulele with this casual group.All skill levels are welcome. If needed, you can borrow a ukulele with your Idea Exchange membership.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Ukulele |Music |Meet-Up |Instruments |Culture Days |
}
\vspace{10px}

\subtitle{Practice Your English}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642121}
\vspace{10px}

Meet new friends, learn about your community, share your culture and customs, and practice your English.Join us for casual conversation and connection led by experienced and friendly Cambridge Public Library volunteers.These weekly sessions cover various topics featuring group activities and one-on-one or one-on-two practice in a fun and helpful environment.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Learn English |Language |ESL |Conversation |
}
\vspace{10px}

\subtitle{PJ Tales}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642450}
\vspace{10px}

Wear your pajamas and bring a stuffie to this evening storytime for families.Hear a bedtime story, sing songs, and make a craft to take home.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |School Aged |Preschool |
}
\vspace{10px}

\headline{October 09, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806609}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806755}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806971}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807108}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Totstime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642530}
\vspace{10px}

Dance, sing, rhyme, and craft with your tot.Enjoy stories, songs, and movement. An excellent program to meet other children and caregivers in your community.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Sensory Tales}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11646999}
\vspace{10px}

All the senses are celebrated in this inclusive sensory experience.Experience an immersive sensory story time filled with adventure.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Preschool |
}
\vspace{10px}

\subtitle{Hespeler Knitting Circle}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11424522}
\vspace{10px}

Share your ideas and creations with fellow knitters.Whether you’re an expert, or just starting out, everyone is welcome to participate, or just have some friendly conversation.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Programs + Workshops |Maker Programs |TAGS: |Knitting |Culture Days |Arts |
}
\vspace{10px}

\subtitle{Totstime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642516}
\vspace{10px}

Dance, sing, rhyme, and craft with your tot.Enjoy stories, songs, and movement. An excellent program to meet other children and caregivers in your community.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Baby Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498387}
\vspace{10px}

Get ready for some circle time fun!Learn new songs and rhymes, share stories, and meet other caregivers. At the same time, your little one will discover the exciting world around them. Baby Connections is a free community program that provides each family with a take-home kit of resources.Please only register once in your baby's first year.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605200}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605088}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{Cambridge Oktoberfest Lunch}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-10-09-1130-Cambridge-Oktoberfest-Lunch}
\vspace{10px}

Mayor Jan Liggett, City Council and Enbridge invite you to join them for the annual Cambridge Oktoberfest lunch!Wednesday, October 9 from 11:30am - 1:30pm at City Hall, 50 Dickson StreetEnjoy a FREE sausage with sauerkraut (while supplies last), Bavarian music, keg tapping and a visit with Onkel Hans and Tante Frieda!
}
\vspace{10px}

\subtitle{Connections 50+ Hespeler}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11516782}
\vspace{10px}

This older adult-focused program features a variety of entertaining activities such as local musicians, guest speakers, art activities, and much more.Guess the song and fill out your bingo card to win! This musical bingo will focus on songs from pop culture, such as TV show theme songs, movie soundtracks and scores, and commercial jingles.Upcoming Connections 50+ Events at HespelerOctober 23: Intro to Painting with VirginiaNovember 6: Generative Artificial Intelligence with guest speaker Amanda TkaczykNovember 20: Guest Speaker: Wildlife Photographer Paul GainsAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign
}
\vspace{10px}

\subtitle{Maker Madness}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11641366}
\vspace{10px}

Enjoy this fun crafternoon with us while we make... anything!Try out some new skills with a different hands-on activity each week.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Activities |
}
\vspace{10px}

\subtitle{Afternoon Craft Club}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498158}
\vspace{10px}

Enjoy games, activities, crafts, and yummy snacks.Get crafty with a new project each week after school. Light refreshments will be provided.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Games |Crafts |
}
\vspace{10px}

\subtitle{Practice Your English}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642178}
\vspace{10px}

Meet new friends, learn about your community, share your culture and customs, and practice your English.Join us for casual conversation and connection led by experienced and friendly Cambridge Public Library volunteers.These weekly sessions cover various topics featuring group activities and one-on-one or one-on-two practice in a fun and helpful environment.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Learn English |Language |ESL |Conversation |
}
\vspace{10px}

\subtitle{Fibre Arts Meet-Up}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11447873}
\vspace{10px}

Join other fibre arts enthusiasts as you work on your own project in a social environment.Share ideas and tips with like-minded folks related to knit, crochet, embroidery, macrame, sewing, and other fibre arts for a weekly social meet-up.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |Maker Programs |TAGS: |Fibre |Culture Days |Crafts |Arts |
}
\vspace{10px}

\headline{October 10, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806610}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806756}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806972}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807109}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Community Desk: Welcome YMCA Immigrant Services}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11502125}
\vspace{10px}

As a primary settlement agency in Cambridge, YMCA Immigrant Services acts as a “first stop” for newcomers.Through the YMCA Library Settlement Partnerships (LSP), our Settlement Workers are located within the libraries to continue to support newcomer and immigrant needs. Our Settlement Workers can provide support with citizenship, housing, education, English language assessments, connecting with community resources, and much more. Through our collaboration with Idea Exchange, together we are working to foster a smooth transition into the Cambridge community.The Library Settlement Partnership program is a partnership of Idea Exchange, the YMCA’s Immigrant Services Program, and Immigration, Refugees, and Citizenship Canada (IRCC).Services Offered·  Virtual settlement support to newcomers·  Information sessions relevant to newcomer needs in collaboration with Idea Exchange·  LSP staff provide orientation to library services and referrals·  Services available virtually, over the phone, and 
}
\vspace{10px}

\subtitle{Totstime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642540}
\vspace{10px}

Dance, sing, rhyme, and craft with your tot.Enjoy stories, songs, and movement. An excellent program to meet other children and caregivers in your community.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{The Imagination Station}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11667658}
\vspace{10px}

Let your imagination run wild!From playing dress-up to flying in a make-believe airplane, children will have the opportunity to explore themselves and the world around them.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |
}
\vspace{10px}

\subtitle{Stories and Stretches}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642582}
\vspace{10px}

Stretch it out and get your body moving.Come enjoy this unique program with its combination of stories, movement activities, and fun!AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |School Aged |Preschool |Activities |
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605155}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{Homeschool Makers}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11640496}
\vspace{10px}

An interactive opportunity to explore a wide range of maker equipment.From innovative technologies to traditional art forms, explore something new each week.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |Maker Programs |TAGS: |Technology |Arts |
}
\vspace{10px}

\subtitle{Homeschool Heroes}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11610724}
\vspace{10px}

Calling all heroes! This program teaches kids that empathy can make us all heroes.We will read stories, play games, and finish each week with a craft.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |Games |Crafts |
}
\vspace{10px}

\subtitle{Preschool Picassos}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642473}
\vspace{10px}

Draw out your child's inner Picasso with amazing art projects.Each week, you and your child will use imagination and fun art supplies to explore and create. Please dress to get messy.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |Arts |
}
\vspace{10px}

\subtitle{Practice Your English}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642164}
\vspace{10px}

Meet new friends, learn about your community, share your culture and customs, and practice your English.Join us for casual conversation and connection led by experienced and friendly Cambridge Public Library volunteers.These weekly sessions cover various topics featuring group activities and one-on-one or one-on-two practice in a fun and helpful environment.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Learn English |Language |ESL |Conversation |
}
\vspace{10px}

\subtitle{Families Under the Rainbow}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11635775}
\vspace{10px}

In collaboration with SPECTRUM Waterloo Region's Rainbow Community Space.Read along with stories, make crafts, and have fun playing together in a safe and supported environment for 2SLGBTQ+ youth, families, and allies.This program is generously funded by a grant from the Lyle S. Hallman foundation.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |SPECTRUM |Queer |Preschool |2SLGBTQIA+ |
}
\vspace{10px}

\subtitle{Learn to Crochet: Mini Pumpkin}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11448647}
\vspace{10px}

Get ready for autumn. Learn basic crochet stitches while making a mini crocheted pumpkin.Crochet your own mini pumpkin while learning the half-double crochet stitch, chain stitch, and slip stitch. Learn about basic tools and resources to continue your crochet crafting journey.All materials and hooks will be provided.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |Maker Programs |TAGS: |Maker |Fibre |Culture Days |Crafts |Crafting |
}
\vspace{10px}

\subtitle{DIY Weaving Workshop}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11634114}
\vspace{10px}

Create your own loom and weave a coaster.Learn how to weave by creating a basic loom and making a coaster out of reclaimed fabric.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |CAGE |Arts |
}
\vspace{10px}

\subtitle{Silent Book Club}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11448812}
\vspace{10px}

Read your book silently alongside other silent readers.Set aside an hour of dedicated time to read while you share a quiet space with other readers. Share a little bit about what you're reading or listen to recommendations from other readers.There is no homework and sharing is optional. Bring your book in any format. This is a drop-in program, you do not need to register to attend.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Book Clubs |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Ukulele Meet-Up}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11424373}
\vspace{10px}

Enjoy singing and smiling while strumming your ukulele with this casual group.All skill levels are welcome. If needed, you can borrow a ukulele with your membership.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Ukulele |Music |Meet-Up |Instruments |Culture Days |
}
\vspace{10px}

\subtitle{Next in Soldering: 6-Digit LED Digital Clock}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11685671}
\vspace{10px}

Learn basic soldering skills in this two-week program.Learn to solder a simple LED Digital Clock. You will leave with your completed project at the end of the second session.Participants must provide a signed waiver to participate in this program.Cost: \$12.00 + HST to cover the cost of materials supplied.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.AGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |Maker Programs |TAGS: |Tech |
}
\vspace{10px}

\subtitle{Crafty Kids}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11557298}
\vspace{10px}

Get crafty!Get inspired by a story and then explore your creativity with unique crafts and art projects each week.Materials will be provided.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Crafts |Crafting |Arts |
}
\vspace{10px}

\subtitle{Bloody Berlin Walking Tour}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-10-10-1900-Bloody-Berlin-Walking-Tour}
\vspace{10px}

Join Schneider Haus staff for an evening walk through the back alleys and side streets of downtown Kitchener as we talk about some of the scary, sexy, or just plain weird characters that have called our town home. Murders, executions, grave robbing, shootouts, villainous doctors, and even pandemics of the past. Come learn a little more about Bloody Berlin….if you dare!Kick start your spooky season with us on Friday the 13th in September! There's no better time to learn about bloody Berlin than on the unluckiest day of the year!Admission:\$31 per person plus HST. Advance ticket purchase is required for this event, there will be no tickets sold at the door. Membership discount applies. No refunds.Information about Event:Suitable for ages 16 and up.Event runs rain or shine. This event takes place entirely outdoors and there will be no access to washrooms. The Historic Haus and galleries will be closed.Participants should dress for the weather and bring a flashlight (if possible).Please not
}
\vspace{10px}

\headline{October 11, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806611}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806757}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806973}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807110}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Schneider Haus October PD Day Camp}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-10-11-0830-Schneider-Haus-October-PD-Day-Camp}
\vspace{10px}

Join us at Schneider Haus for a day of engaging activities, with plenty of time outdoors, on October 11th! Programming provides a mix of free and structured play, allowing children to explore, create, build, dig, discover, and make new friends. Campers must bring a lunch and snacks. Food will not be provided. Please ensure your child is dressed for the unpredictable Fall weather!Age range: Children from 5 to 10 years old.Times: Drop off - 8:30 to 9:00 a.m. & Pick up – 4:00 to 4:30 p.m.Cost: \$50 per day per childUnfortunately we are unable to accomodate earlier drop off times or later pick up times.
}
\vspace{10px}

\subtitle{Old Post Office Book Club}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11627623}
\vspace{10px}

Meet monthly to discuss a pre-selected title, share thoughts, and learn more about the books we love.This season's book titles:While supplies last, pick up a copies of the next month's book from the Old Post Office starting the second Friday of the month prior.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Book Clubs |TAGS: | |
}
\vspace{10px}

\subtitle{PD Day Stay and Play}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11610958}
\vspace{10px}

Come and stay and play!Join children and other caregivers while they explore stations throughout the children's area.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{Kindness Rocks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11640515}
\vspace{10px}

Sing, dance, and practice self-confidence.It's time to sing and dance together to celebrate kindness! This music-based program encourages self-confidence as your little one practices new skills.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Singing |Preschool |Music |Dancing |
}
\vspace{10px}

\subtitle{Community Desk: Welcome YMCA Immigrant Services}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11502151}
\vspace{10px}

As a primary settlement agency in Cambridge, YMCA Immigrant Services acts as a “first stop” for newcomers.Through the YMCA Library Settlement Partnerships (LSP), our Settlement Workers are located within the libraries to continue to support newcomer and immigrant needs. Our Settlement Workers can provide support with citizenship, housing, education, English language assessments, connecting with community resources, and much more. Through our collaboration with Cambridge Public Library (formerly Idea Exchange), together we are working to foster a smooth transition into the Cambridge community.The Library Settlement Partnership program is a partnership of Idea Exchange, the YMCA’s Immigrant Services Program, and Immigration, Refugees, and Citizenship Canada (IRCC).Services Offered·  Virtual settlement support to newcomers·  Information sessions relevant to newcomer needs in collaboration with Cambridge Public Library (formerly Idea Exchange)·  LSP staff provide orientation to library ser
}
\vspace{10px}

\subtitle{Art Cart: Weaving}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11760458}
\vspace{10px}

Drop in to create a unique craft!Learn how to weave by creating a basic loom and making a coaster out of reclaimed fabric.Presented by CAGE:AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |Cambridge Art Galleries |EVENT TYPE: |Programs + Workshops |TAGS: |Culture Days |Crafts |CAGE |Arts |
}
\vspace{10px}

\subtitle{Baby Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498374}
\vspace{10px}

Get ready for some circle time fun!Learn new songs and rhymes, share stories, and meet other caregivers. At the same time, your little one will discover the exciting world around them. Baby Connections is a free community program that provides each family with a take-home kit of resources.Please only register once in your baby's first year.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Connections 50+ Queen's Square}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11597523}
\vspace{10px}

Connect with other adults while enjoying concerts, crafting, chats, and more.Advance Care Planning 101Regardless of a person’s age or health status, serious accidents, and sudden health changes can happen. Imagine you are unable to make your own healthcare decisions, who would decide for you?Learn about health care decision making in Ontario and how Advance Care Planning conversations can help you and your loved ones. This session is all about how the law in Ontario sets up Substitute Decision Making, and what you need to know about choosing your Substitute Decision Maker. This is essential information you need to know about Advance Care Planning in Ontario.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending 
}
\vspace{10px}

\subtitle{Stories and Stretches}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642623}
\vspace{10px}

Stretch it out and get your body moving.Come enjoy this unique program with its combination of stories, movement activities, and fun!AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |School Aged |Preschool |Activities |
}
\vspace{10px}

\subtitle{Community Desk: Welcome WRSPC}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11639826}
\vspace{10px}

Learn about resources for how you can help yourself, someone else, and coping with suicide loss.The Waterloo Region Suicide Prevention Council is a community-based non-profit aiming to increase awareness of and engagement in suicide prevention within our community to ultimately reduce suicide and its impact. We do so through education, training, and community engagement initiatives utilizing suicide prevention and positive life promotion messaging.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Newcomers |Kids |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Men
}
\vspace{10px}

\subtitle{"The Dark Side of Galt" Evening Walking Tours}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-10-11-1830-The-Dark-Side-of-Galt-Evening-Walking-Tours}
\vspace{10px}

Put on your comfy walking shoes and join us as we take a summer stroll through the past, exploring stories of disasters, hauntings, murders and other unsavoury events that are part of the make up of Galt's dark history.Please note: Tours begin at 6:30 p.m. and 7:00 p.m. each night and run for approximately 90-minutes, departing from, and finishing up at McDougall Cottage.The tours may include hills, stairs and uneven terrain. Participants should dress for the weather. Phones are recommended, but not required, to access photos of the sites we are visiting. No washroom facilities available during tour.Ages 14 + only.October 18th Special Event - On October 18th there will be special tickets for any members of our walk who want to finish off the evening with a beverage and evening at Cafe 13 Food & Beverage. The special ticket price includes one 20oz beer, 6oz wine or feature cocktail, and cover waived (normal \$5) for the upstairs Taproom “Sisters of Salem” Dress Up Party featuring live mu
}
\vspace{10px}

\headline{October 12, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806612}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806758}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806974}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807111}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Cambridge Farmers' Market}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-10-12-0700-Cambridge-Farmers-Market}
\vspace{10px}

The Cambridge Farmers' Market is open year round 7am-1pm.We have something for everyone! Hot-prepared foods, meats,seafood, cheese,chutneys, pies, confections, preserves and seasonal vegetables.
}
\vspace{10px}

\subtitle{Practice Your English}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642142}
\vspace{10px}

Meet new friends, learn about your community, share your culture and customs, and practice your English.Join us for casual conversation and connection led by experienced and friendly Cambridge Public Library volunteers.These weekly sessions cover various topics featuring group activities and one-on-one or one-on-two practice in a fun and helpful environment.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Learn English |Language |ESL |Conversation |
}
\vspace{10px}

\subtitle{An Evening with The Paranormal Seekers}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-10-12-1900-An-Evening-with-The-Paranormal-Seekers}
\vspace{10px}

It’s that time of year when our thoughts turn to the spirit realm...Join us for another fascinating presentation by paranormal investigators, The Paranormal Seekers.Alongside stories of who they are, what they do and why they do it, they’ll be showcasing some of the tools and techniques that they use in their investigations of phenomena beyond the scope of normal scientific understanding.Believer, or skeptic, all are welcome to bring along questions and/or stories of your own encounters with the paranormal!Cost is \$12.50 per person, plus HST. Registration is required.
}
\vspace{10px}

\subtitle{Bloody Berlin Walking Tour}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-10-12-1900-Bloody-Berlin-Walking-Tour}
\vspace{10px}

Join Schneider Haus staff for an evening walk through the back alleys and side streets of downtown Kitchener as we talk about some of the scary, sexy, or just plain weird characters that have called our town home. Murders, executions, grave robbing, shootouts, villainous doctors, and even pandemics of the past. Come learn a little more about Bloody Berlin….if you dare!Kick start your spooky season with us on Friday the 13th in September! There's no better time to learn about bloody Berlin than on the unluckiest day of the year!Admission:\$31 per person plus HST. Advance ticket purchase is required for this event, there will be no tickets sold at the door. Membership discount applies. No refunds.Information about Event:Suitable for ages 16 and up.Event runs rain or shine. This event takes place entirely outdoors and there will be no access to washrooms. The Historic Haus and galleries will be closed.Participants should dress for the weather and bring a flashlight (if possible).Please not
}
\vspace{10px}

\headline{October 13, 2024}

\subtitle{Thanksgiving Closure}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/9567550}
\vspace{10px}

All Idea Exchange locations will be closed October 13 and 14 for Thanksgiving.Though our buildings are closed, you can access our online resources such as eBooks, audiobook, magazines, movies, and educational materials at any time. If you are not currently a member, sign-up for a free online membership to start borrowing digital materials and accessing online resources.Items can be renewed online or over the telephone (519-740-3000) while we are closed.You can also visit the Cambridge Art Galleries online to view the Fibre Art Collection digitally.AGE GROUP: |Teens |Newcomers |Kids |Cambridge Art Galleries |Adults |EVENT TYPE: |Special Events |TAGS: | |
}
\vspace{10px}

\headline{October 14, 2024}

\subtitle{Thanksgiving Closure}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/9567551}
\vspace{10px}

All Idea Exchange locations will be closed October 13 and 14 for Thanksgiving.Though our buildings are closed, you can access our online resources such as eBooks, audiobook, magazines, movies, and educational materials at any time. If you are not currently a member, sign-up for a free online membership to start borrowing digital materials and accessing online resources.Items can be renewed online or over the telephone (519-740-3000) while we are closed.You can also visit the Cambridge Art Galleries online to view the Fibre Art Collection digitally.AGE GROUP: |Teens |Newcomers |Kids |Cambridge Art Galleries |Adults |EVENT TYPE: |Special Events |TAGS: | |
}
\vspace{10px}

\subtitle{Community Desk: Welcome Kinbridge!}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11634038}
\vspace{10px}

Are you a newcomer trying to get ready for the Canadian workforce? Kinbridge is here to help.Kinbridge's Newcomer Employment Outreach offers support with resume and cover letter writing, interview preparation, job search advice, and integrating into the Canadian workplace.Drop in or contact Lily Magnus to book an appointment for referrals to workshops and training.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |EVENT TYPE: |Programs + Workshops |TAGS: |Resume |Jobs |Interviews |Employment |Cover Letter |Community |Careers |
}
\vspace{10px}

\subtitle{Craft Stop}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11669924}
\vspace{10px}

Make a different craft each week.This social gathering is a fun way to show off your creative side and make something amazing.All materials provided.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Crafts |
}
\vspace{10px}

\headline{October 15, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806613}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806759}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806975}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807112}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Community Desk: Welcome YMCA Immigrant Services}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11502101}
\vspace{10px}

As a primary settlement agency in Cambridge, YMCA Immigrant Services acts as a “first stop” for newcomers.Through the YMCA Library Settlement Partnerships (LSP), our Settlement Workers are located within the libraries to continue to support newcomer and immigrant needs. Our Settlement Workers can provide support with citizenship, housing, education, English language assessments, connecting with community resources, and much more. Through our collaboration with Idea Exchange, together we are working to foster a smooth transition into the Cambridge community.The Library Settlement Partnership program is a partnership of Idea Exchange, the YMCA’s Immigrant Services Program, and Immigration, Refugees, and Citizenship Canada (IRCC).Services Offered·  Virtual settlement support to newcomers·  Information sessions relevant to newcomer needs in collaboration with Idea Exchange·  LSP staff provide orientation to library services and referrals·  Services available virtually, over the phone, and 
}
\vspace{10px}

\subtitle{Kindergarten Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11610620}
\vspace{10px}

Get ready for Kindergarten!Children will learn fundamental skills while having fun and meeting new friends.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |
}
\vspace{10px}

\subtitle{Stories and Stretches}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642605}
\vspace{10px}

Stretch it out and get your body moving.Come enjoy this unique program with its combination of stories, movement activities, and fun!AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |School Aged |Preschool |Activities |
}
\vspace{10px}

\subtitle{Art Cart}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11447833}
\vspace{10px}

Drop in to create a unique craft!Colour a drawing, make a collage, build a sculpture! Try something new each time you visit the Cambridge Art Gallery Education Art Cart.Presented by CAGE:AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |Cambridge Art Galleries |EVENT TYPE: |Programs + Workshops |TAGS: |Culture Days |CAGE |Arts |
}
\vspace{10px}

\subtitle{Preschool Picassos}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642486}
\vspace{10px}

Draw out your child's inner Picasso with amazing art projects.Each week, you and your child will use imagination and fun art supplies to explore and create. Please dress to get messy.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |Arts |
}
\vspace{10px}

\subtitle{STEAM Storytime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11666706}
\vspace{10px}

Twinkle, twinkle, little star, how I wonder what you are…Songs, rhymes, stories, and fun learning activities that inspire curious little minds to explore STEAM (science, technology, engineering, art, and math) and more.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |School Aged |Preschool |
}
\vspace{10px}

\subtitle{Baby Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498402}
\vspace{10px}

Get ready for some circle time fun!Learn new songs and rhymes, share stories, and meet other caregivers. At the same time, your little one will discover the exciting world around them. Baby Connections is a free community program that provides each family with a take-home kit of resources.Please only register once in your baby's first year.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Kindergarten Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11610689}
\vspace{10px}

Get ready for Kindergarten!Children will learn fundamental skills while having fun and meeting new friends.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Kindergarten |
}
\vspace{10px}

\subtitle{Art Through the Ages}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498237}
\vspace{10px}

Explore history from the 1920s-2020s through music, fashion, toys, and more.Together, we will make crafts, play games, and immerse ourselves in history.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Arts |
}
\vspace{10px}

\subtitle{Reading Buddies}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11646929}
\vspace{10px}

Kids practice their reading with a teenage buddy.This program is designed for children struggling to read at their grade level. Reading skills will be developed and practiced through fun and interactive literacy-based group games and activities. Children will also have the opportunity to read one-on-one with their teen volunteer buddy.Teens interested in becoming a Reading Buddy must complete our online volunteer application form. They will be contacted for an interview and orientation by our volunteer coordinator.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |
}
\vspace{10px}

\subtitle{Paws for Reading}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642193}
\vspace{10px}

Join our furry four-legged friends from Lions Club dog guides for the ultimate reading practice program.Children learn about service dogs from volunteers and then read to the doggies.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Animals |
}
\vspace{10px}

\subtitle{Recycle It!}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11666453}
\vspace{10px}

Discover the art of upcycling while turning your trash into treasure.This craft-based program will teach kids how to take everyday items and transform them in new and innovative ways.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Crafts |Arts |
}
\vspace{10px}

\subtitle{Galt Chess Club}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11799628}
\vspace{10px}

Fall adult drop-in chess club.Play the world's most popular board game with fellow chess enthusiasts. Boards and game pieces will be provided, but if you have your own set, you are welcome to bring it along.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Chess |Board Games |
}
\vspace{10px}

\subtitle{Learn Morse Code with Cambridge Amateur Radio}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11685677}
\vspace{10px}

Learn this well-known code used in amateur radio, aviation, and the military.Join members of the Cambridge Amateur Radio Club in an eight-week series of classes that will teach you to use Morse code and some of the history behind it.Morse code, or CW as known among amateur radio operators, is using a combination of short and long ‘beeps’ of a tone. The number and the combination of short and long ‘beeps’ will signify a letter. You will be surprised at how quickly you adapt to sense the difference among the various combinations and translate it to a letter, forming words and sentences. Learning Morse code is a great way to challenge your mind and keep it sharp.Amateur Radio (ham radio) is a popular hobby and service that brings people, electronics, and communication together. People use amateur radio to talk across town, around the world, or even into space, all without the Internet or cell phones. It's fun, social, educational, and can be a lifeline during times of need.This program ru
}
\vspace{10px}

\subtitle{Ukulele Meet-Up}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11424419}
\vspace{10px}

Enjoy singing and smiling while strumming your ukulele with this casual group.All skill levels are welcome. If needed, you can borrow a ukulele with your Idea Exchange membership.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Ukulele |Music |Meet-Up |Instruments |Culture Days |
}
\vspace{10px}

\subtitle{Employment Skill Building}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11558361}
\vspace{10px}

Join Starling Employment Services (formerly Lutherwood) for this free, open workshop series to build your job searching skills.Each session will provide information and practical tips on a different employment topic including goal setting, resumes, networking, interviews, and more. Choose a session that grabs your interest or join us for the entire series. We are looking forward to seeing you and giving you a taste of what Starling's Employment Services has to offer. Come take the next step of your job search journey with us.This week's topic is:Cover Letters and Networking: Let's talk about these two misunderstood resources in the job seeker's toolkit. We'll de-mystify them together with some practical steps to marketing yourself and making professional connections.Tuesday, September 17: Job Search Preparation and Goal SettingTuesday, October 1: Resume FoundationsTuesday, October 15: Cover Letters and NetworkingTuesday, October 29: Interviewing with ConfidenceTuesday, November 12: You
}
\vspace{10px}

\subtitle{Practice Your English}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642122}
\vspace{10px}

Meet new friends, learn about your community, share your culture and customs, and practice your English.Join us for casual conversation and connection led by experienced and friendly Cambridge Public Library volunteers.These weekly sessions cover various topics featuring group activities and one-on-one or one-on-two practice in a fun and helpful environment.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Learn English |Language |ESL |Conversation |
}
\vspace{10px}

\subtitle{PJ Tales}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642451}
\vspace{10px}

Wear your pajamas and bring a stuffie to this evening storytime for families.Hear a bedtime story, sing songs, and make a craft to take home.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |School Aged |Preschool |
}
\vspace{10px}

\subtitle{Youth Advisory Committee}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11668610}
\vspace{10px}

Teens can join the Youth Advisory Committee (YAC).YAC helps to make the library a special place for teens. As a member of YAC, you have a chance to have your say, become involved in the community, and meet new friends. YAC members earn volunteer hours for attending meetings.At meetings, you can:AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |EVENT TYPE: |Programs + Workshops |TAGS: |Community |
}
\vspace{10px}

\subtitle{UnBook Club}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11668185}
\vspace{10px}

With no set book to read, this club is about great conversation and good fun!Meet new people, get awesome recommendations, and chat about what you've been reading, watching, or listening to.Note: This event is held at a different restaurant in Cambridge each time. Members can buy their own food and drink but the club is free.AGE GROUP: |Adults |EVENT TYPE: |Book Clubs |TAGS: |Community |
}
\vspace{10px}

\headline{October 16, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806614}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806760}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806976}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807113}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Totstime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642531}
\vspace{10px}

Dance, sing, rhyme, and craft with your tot.Enjoy stories, songs, and movement. An excellent program to meet other children and caregivers in your community.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Sensory Tales}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11647000}
\vspace{10px}

All the senses are celebrated in this inclusive sensory experience.Experience an immersive sensory story time filled with adventure.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Preschool |
}
\vspace{10px}

\subtitle{Hespeler Knitting Circle}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11424523}
\vspace{10px}

Share your ideas and creations with fellow knitters.Whether you’re an expert, or just starting out, everyone is welcome to participate, or just have some friendly conversation.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Programs + Workshops |Maker Programs |TAGS: |Knitting |Culture Days |Arts |
}
\vspace{10px}

\subtitle{Totstime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642517}
\vspace{10px}

Dance, sing, rhyme, and craft with your tot.Enjoy stories, songs, and movement. An excellent program to meet other children and caregivers in your community.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Baby Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498388}
\vspace{10px}

Get ready for some circle time fun!Learn new songs and rhymes, share stories, and meet other caregivers. At the same time, your little one will discover the exciting world around them. Baby Connections is a free community program that provides each family with a take-home kit of resources.Please only register once in your baby's first year.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605201}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605089}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{YEAH! Newcomer Youth Group}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11696767}
\vspace{10px}

A place to meet new people, make new connections, and play games, activities, and sports.YEAH! - Youth Empowerment and Healing is a newcomer youth group for refugee and protected teens to support one another and share experiences that matter to you in a safe and encouraging environment. We want to hear what you're interested in and we will share ideas and resources together to help you reach your goals.To register for this eight-week group, please email groups@caminowellbeing.ca or phone 519-743-6333.About our PartnersCamino Wellbeing + Mental Health unites the work of Carizon Family and Community Services, KW Counselling Services, and Monica Place all under one umbrella. Together, they create a more cohesive system that brings greater impact to our community's growing wellbeing and mental health needs.They provide tools, resources and services that help people reach their full potential as they walk the path to achieving their best wellbeing and mental health.AccessibilityIf you requi
}
\vspace{10px}

\subtitle{Maker Madness}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11641367}
\vspace{10px}

Enjoy this fun crafternoon with us while we make... anything!Try out some new skills with a different hands-on activity each week.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Activities |
}
\vspace{10px}

\subtitle{Afternoon Craft Club}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498159}
\vspace{10px}

Enjoy games, activities, crafts, and yummy snacks.Get crafty with a new project each week after school. Light refreshments will be provided.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Games |Crafts |
}
\vspace{10px}

\subtitle{Teen Makers to Market}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11667433}
\vspace{10px}

Attention Cambridge teen artists and makers! In this program, learn about turning your creative talents into a business that will prepare you to be a craft market vendor.Learn the ins and outs of product development, marketing, sales, and so much more, through weekly training and co-working sessions that include hands-on time in our Makerspace.By the end of this program, you should know enough to participate in a craft market. Don't miss this unique opportunity to turn your passion into profit.Our program lead will reach out to registrants before Wednesday, October 16 to learn more about what you hope to achieve from the program.Register by Monday, September 30.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attend
}
\vspace{10px}

\subtitle{Collaborative Comics}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11502012}
\vspace{10px}

Whether comics or manga, come together to draw some unscripted, improvised sequential art.Artists of all skill levels are invited to create a panel and pass it on to the next person to see where these comic stories take us.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Writing |Manga |Drawing |Comics |Arts |
}
\vspace{10px}

\subtitle{Practice Your English}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642179}
\vspace{10px}

Meet new friends, learn about your community, share your culture and customs, and practice your English.Join us for casual conversation and connection led by experienced and friendly Cambridge Public Library volunteers.These weekly sessions cover various topics featuring group activities and one-on-one or one-on-two practice in a fun and helpful environment.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Learn English |Language |ESL |Conversation |
}
\vspace{10px}

\subtitle{Fibre Arts Meet-Up}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11447874}
\vspace{10px}

Join other fibre arts enthusiasts as you work on your own project in a social environment.Share ideas and tips with like-minded folks related to knit, crochet, embroidery, macrame, sewing, and other fibre arts for a weekly social meet-up.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |Maker Programs |TAGS: |Fibre |Culture Days |Crafts |Arts |
}
\vspace{10px}

\headline{October 17, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806615}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806761}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806977}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807114}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Community Desk: Welcome YMCA Immigrant Services}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11502126}
\vspace{10px}

As a primary settlement agency in Cambridge, YMCA Immigrant Services acts as a “first stop” for newcomers.Through the YMCA Library Settlement Partnerships (LSP), our Settlement Workers are located within the libraries to continue to support newcomer and immigrant needs. Our Settlement Workers can provide support with citizenship, housing, education, English language assessments, connecting with community resources, and much more. Through our collaboration with Idea Exchange, together we are working to foster a smooth transition into the Cambridge community.The Library Settlement Partnership program is a partnership of Idea Exchange, the YMCA’s Immigrant Services Program, and Immigration, Refugees, and Citizenship Canada (IRCC).Services Offered·  Virtual settlement support to newcomers·  Information sessions relevant to newcomer needs in collaboration with Idea Exchange·  LSP staff provide orientation to library services and referrals·  Services available virtually, over the phone, and 
}
\vspace{10px}

\subtitle{Totstime}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642541}
\vspace{10px}

Dance, sing, rhyme, and craft with your tot.Enjoy stories, songs, and movement. An excellent program to meet other children and caregivers in your community.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{The Imagination Station}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11667659}
\vspace{10px}

Let your imagination run wild!From playing dress-up to flying in a make-believe airplane, children will have the opportunity to explore themselves and the world around them.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Preschool |
}
\vspace{10px}

\subtitle{Stories and Stretches}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642583}
\vspace{10px}

Stretch it out and get your body moving.Come enjoy this unique program with its combination of stories, movement activities, and fun!AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |School Aged |Preschool |Activities |
}
\vspace{10px}

\subtitle{Explore on the Floor}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11605156}
\vspace{10px}

Let's Play!Let your little one play, discover, and explore in a variety of fun-filled, hands-on learning activity centers.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |
}
\vspace{10px}

\subtitle{Homeschool Makers}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11640497}
\vspace{10px}

An interactive opportunity to explore a wide range of maker equipment.From innovative technologies to traditional art forms, explore something new each week.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |Maker Programs |TAGS: |Technology |Arts |
}
\vspace{10px}

\subtitle{Homeschool Heroes}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11610725}
\vspace{10px}

Calling all heroes! This program teaches kids that empathy can make us all heroes.We will read stories, play games, and finish each week with a craft.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |Games |Crafts |
}
\vspace{10px}

\subtitle{Preschool Picassos}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642474}
\vspace{10px}

Draw out your child's inner Picasso with amazing art projects.Each week, you and your child will use imagination and fun art supplies to explore and create. Please dress to get messy.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Stem |Steam |Preschool |Arts |
}
\vspace{10px}

\subtitle{Retro Gaming}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11596739}
\vspace{10px}

Gaming fun with a retro twist!Everyone who loves board games, video games, and having fun is welcome to join us to play a variety of retro games.This program is presented in partnership with OPERANDi Gaming Community.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Video Games |Retro Gaming |Gaming |Gamer |Board Games |
}
\vspace{10px}

\subtitle{Introduction to Laser Cutting}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11640720}
\vspace{10px}

Interested in using a laser cutter but have no idea where to start?Learn the basics of 2D design using CorelDraw, specifically with the laser cutter in-mind. We will also teach you to draw vector lines, cut out shapes and letters, and saving the design. When finished, you will have the skills to make designs for cutting and engraving.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Maker Programs |TAGS: |Technology |Makerspace |DIY |
}
\vspace{10px}

\subtitle{Practice Your English}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642165}
\vspace{10px}

Meet new friends, learn about your community, share your culture and customs, and practice your English.Join us for casual conversation and connection led by experienced and friendly Cambridge Public Library volunteers.These weekly sessions cover various topics featuring group activities and one-on-one or one-on-two practice in a fun and helpful environment.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Learn English |Language |ESL |Conversation |
}
\vspace{10px}

\subtitle{Families Under the Rainbow}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11635776}
\vspace{10px}

In collaboration with SPECTRUM Waterloo Region's Rainbow Community Space.Read along with stories, make crafts, and have fun playing together in a safe and supported environment for 2SLGBTQ+ youth, families, and allies.This program is generously funded by a grant from the Lyle S. Hallman foundation.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |SPECTRUM |Queer |Preschool |2SLGBTQIA+ |
}
\vspace{10px}

\subtitle{SPECTRUM Cambridge Transgender Peer Support Group}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/10940718}
\vspace{10px}

Join SPECTRUM for a discussion and to meet other local gender-diverse folks.Funded by a grant from the Cambridge and North Dumfries Community Foundation, the biweekly Cambridge Transgender Peer Support Group is an informal, discussion-based, drop-in program. This group is a space for adults that identify within the trans/gender variant umbrella.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |SPECTRUM |Queer |Pride |2SLGBTQIA+ |
}
\vspace{10px}

\subtitle{Queer Craft Circle}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11760886}
\vspace{10px}

LGBTQ2S+ identifying individuals are invited to explore a different creative project each month in a fun and safe space.Join us for this fun, casual program. Together we will explore a new creative project with a guest artist each month. Registration is limited to 2SLGBTQ+ identifying people in Waterloo Region. This month Trevor Waurechen will demonstrate print making techniques using LEGO.This program is offered in partnership with Spectrum, Waterloo Region's Rainbow Community Space.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeThis program is offered in collaboration with Spectrum, Waterloo
}
\vspace{10px}

\subtitle{Ukulele Meet-Up}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11424374}
\vspace{10px}

Enjoy singing and smiling while strumming your ukulele with this casual group.All skill levels are welcome. If needed, you can borrow a ukulele with your membership.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Ukulele |Music |Meet-Up |Instruments |Culture Days |
}
\vspace{10px}

\subtitle{Next in Soldering: 6-Digit LED Digital Clock}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11685672}
\vspace{10px}

Learn basic soldering skills in this two-week program.Learn to solder a simple LED Digital Clock. You will leave with your completed project at the end of the second session.Participants must provide a signed waiver to participate in this program.Cost: \$12.00 + HST to cover the cost of materials supplied.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.AGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |Maker Programs |TAGS: |Tech |
}
\vspace{10px}

\subtitle{Queer Reading Circle}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11666182}
\vspace{10px}

Fall into 2SLGBTQIA+ stories and more this autumn.The Queer Reading Circle provides a welcoming and safe space for individuals to connect and discuss materials by 2SLGBTQIA+ writers.Join us on the third Thursday of every month for book talks, group readings, discussions of poetry, short stories, and more.There is no need to prepare in advance. All reading materials are provided.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Adults |EVENT TYPE: |Book Clubs |TAGS: |Queer |2SLGBTQIA+ |
}
\vspace{10px}

\subtitle{Crafty Kids}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11557299}
\vspace{10px}

Get crafty!Get inspired by a story and then explore your creativity with unique crafts and art projects each week.Materials will be provided.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |School Aged |Crafts |Crafting |Arts |
}
\vspace{10px}

\subtitle{Bloody Berlin Walking Tour}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-10-17-1900-Bloody-Berlin-Walking-Tour}
\vspace{10px}

Join Schneider Haus staff for an evening walk through the back alleys and side streets of downtown Kitchener as we talk about some of the scary, sexy, or just plain weird characters that have called our town home. Murders, executions, grave robbing, shootouts, villainous doctors, and even pandemics of the past. Come learn a little more about Bloody Berlin….if you dare!Kick start your spooky season with us on Friday the 13th in September! There's no better time to learn about bloody Berlin than on the unluckiest day of the year!Admission:\$31 per person plus HST. Advance ticket purchase is required for this event, there will be no tickets sold at the door. Membership discount applies. No refunds.Information about Event:Suitable for ages 16 and up.Event runs rain or shine. This event takes place entirely outdoors and there will be no access to washrooms. The Historic Haus and galleries will be closed.Participants should dress for the weather and bring a flashlight (if possible).Please not
}
\vspace{10px}

\headline{October 18, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806616}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806762}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806978}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807115}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Kindness Rocks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11640516}
\vspace{10px}

Sing, dance, and practice self-confidence.It's time to sing and dance together to celebrate kindness! This music-based program encourages self-confidence as your little one practices new skills.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Singing |Preschool |Music |Dancing |
}
\vspace{10px}

\subtitle{Community Desk: Welcome YMCA Immigrant Services}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11502152}
\vspace{10px}

As a primary settlement agency in Cambridge, YMCA Immigrant Services acts as a “first stop” for newcomers.Through the YMCA Library Settlement Partnerships (LSP), our Settlement Workers are located within the libraries to continue to support newcomer and immigrant needs. Our Settlement Workers can provide support with citizenship, housing, education, English language assessments, connecting with community resources, and much more. Through our collaboration with Cambridge Public Library (formerly Idea Exchange), together we are working to foster a smooth transition into the Cambridge community.The Library Settlement Partnership program is a partnership of Idea Exchange, the YMCA’s Immigrant Services Program, and Immigration, Refugees, and Citizenship Canada (IRCC).Services Offered·  Virtual settlement support to newcomers·  Information sessions relevant to newcomer needs in collaboration with Cambridge Public Library (formerly Idea Exchange)·  LSP staff provide orientation to library ser
}
\vspace{10px}

\subtitle{Connections 50+ Queen's Square}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11692351}
\vspace{10px}

Connect with other adults while enjoying concerts, crafting, chats, and more.As part of our Connections 50+ suite of programming, this older adult-focused program features a variety of entertaining activities such as local musicians, guest speakers, art activities, and much more.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Seniors |Concert |Community |Arts |
}
\vspace{10px}

\subtitle{Baby Connections}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11498375}
\vspace{10px}

Get ready for some circle time fun!Learn new songs and rhymes, share stories, and meet other caregivers. At the same time, your little one will discover the exciting world around them. Baby Connections is a free community program that provides each family with a take-home kit of resources.Please only register once in your baby's first year.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Baby and Parent |Baby |
}
\vspace{10px}

\subtitle{Stories and Stretches}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642624}
\vspace{10px}

Stretch it out and get your body moving.Come enjoy this unique program with its combination of stories, movement activities, and fun!AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Kids |EVENT TYPE: |Programs + Workshops |TAGS: |Storytime |School Aged |Preschool |Activities |
}
\vspace{10px}

\subtitle{Thrills and Chills Author Evening}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11554306}
\vspace{10px}

Author Nick Cutter discusses The Queen, a heart-pounding novel of terror.The national bestselling author of HorrorBookTok sensation The Troop discusses his new heart-pounding novel of terror, the story of a young woman searching for her missing friend and uncovering a shocking truth.Stop by the Rookery Books table to purchase novels and get them signed by your favourite author as a memento of this thrilling event.Registration is required to confirm attendance. Limited entry without registration may be available at the door.Doors open at 6:00 pmAbout the AuthorNick Cutter is the author of the critically acclaimed national bestseller The Troop (which is currently being developed for film with producer James Wan), The Deep, Little Heaven, and The Handyman Method, co-written with Andrew F. Sullivan. Nick Cutter is the pseudonym for Craig Davidson, whose much-lauded literary fiction includes Rust and Bone, The Saturday Night Ghost Club, and, most recently, the short story collection Cascad
}
\vspace{10px}

\subtitle{"The Dark Side of Galt" Evening Walking Tours}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-10-18-1830-The-Dark-Side-of-Galt-Evening-Walking-Tours}
\vspace{10px}

Put on your comfy walking shoes and join us as we take a summer stroll through the past, exploring stories of disasters, hauntings, murders and other unsavoury events that are part of the make up of Galt's dark history.Please note: Tours begin at 6:30 p.m. and 7:00 p.m. each night and run for approximately 90-minutes, departing from, and finishing up at McDougall Cottage.The tours may include hills, stairs and uneven terrain. Participants should dress for the weather. Phones are recommended, but not required, to access photos of the sites we are visiting. No washroom facilities available during tour.Ages 14 + only.October 18th Special Event - On October 18th there will be special tickets for any members of our walk who want to finish off the evening with a beverage and evening at Cafe 13 Food & Beverage. The special ticket price includes one 20oz beer, 6oz wine or feature cocktail, and cover waived (normal \$5) for the upstairs Taproom “Sisters of Salem” Dress Up Party featuring live mu
}
\vspace{10px}

\headline{October 19, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806617}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806763}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806979}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807116}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Cambridge Farmers' Market}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.cambridge.ca/default/Detail/2024-10-19-0700-Cambridge-Farmers-Market}
\vspace{10px}

The Cambridge Farmers' Market is open year round 7am-1pm.We have something for everyone! Hot-prepared foods, meats,seafood, cheese,chutneys, pies, confections, preserves and seasonal vegetables.
}
\vspace{10px}

\subtitle{Life's a Story}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11803670}
\vspace{10px}

Learn about the lives of people in your community with small group conversations.Each persons journey is a book and at this unique program, you will have the opportunity to listen to personal journeys and converse with three live books from our community. Participate in three small group interactions to expand your knowledge and build understanding with various community members.A Body in Translation by Aashay DalviAashay Dalvi, is an anti-racism consultant for SPECTRUM and founder of Rad Riot Books. They have previously spoken about queer-affirming and anti-colonial literature at the University of Waterloo, the GSA Conference, Tri-Pride, Kitchener Public Library, and more across Waterloo Region.Aashay’s work is guided by the understanding that decolonizing one’s own perspective begins with seeking out and embracing voices that challenge the status quo. Frequently, narratives from queer, racialized, and non-Eurocentric immigrant voices are sidelined or misrepresented in mainstream medi
}
\vspace{10px}

\subtitle{DIY Weaving Workshop}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11634115}
\vspace{10px}

Create your own loom and weave a coaster.Learn how to weave by creating a basic loom and making a coaster out of reclaimed fabric.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |CAGE |Arts |
}
\vspace{10px}

\subtitle{Fun-Filled Fall Family Fiesta!}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-10-19-1100-Fun-Filled-Fall-Family-Fiesta}
\vspace{10px}

All are welcome to join us for an awesome day of games, crafts, treats and more at MCDOUGALL COTTAGE’S FUN-FILLED FALL FAMILY FIESTA as we celebrate our favourite season with fall frolics and Halloween hilarity!There’ll be GAMES – roll, toss and giggle your way through a game of pumpkin bowling, join in the scavenger hunt, or challenge your gang to a skeleton hand ring-toss - CRAFTS – bring out your inner artist with some seasonal creations, and TREATS - No tricks here! All kids who joins us will be gifted some special treats. It’s going to be FALL-TASTIC!Costumes are encouraged, but if costumes aren’t for you, that’s just fine too!And this is a great opportunity to check out our current exhibit Currents of Change: Inspiring Action along the Grand RiverPleaser register in advance and plan to drop in anytime between 11 a.m. to 3:00 p.m. (event ends at 3:30 p.m.). Advance tickets:Children (age 3 years and up): \$10 plus HSTAccompanying Adults: \$5 plus HST(Eventbrite fees apply)Door Price:
}
\vspace{10px}

\subtitle{Board Game Café}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11423634}
\vspace{10px}

A welcoming and friendly atmosphere to play one or more table games.Try a new game, play a classic, or bring one of your favourites with you. From strategy to silly fun, all interest levels are welcome.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Games |Gamer |Culture Days |Board Games |
}
\vspace{10px}

\subtitle{Practice Your English}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11642143}
\vspace{10px}

Meet new friends, learn about your community, share your culture and customs, and practice your English.Join us for casual conversation and connection led by experienced and friendly Cambridge Public Library volunteers.These weekly sessions cover various topics featuring group activities and one-on-one or one-on-two practice in a fun and helpful environment.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Newcomers |Adults |EVENT TYPE: |Programs + Workshops |TAGS: |Learn English |Language |ESL |Conversation |
}
\vspace{10px}

\subtitle{Bloody Berlin Walking Tour}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-10-19-1900-Bloody-Berlin-Walking-Tour}
\vspace{10px}

Join Schneider Haus staff for an evening walk through the back alleys and side streets of downtown Kitchener as we talk about some of the scary, sexy, or just plain weird characters that have called our town home. Murders, executions, grave robbing, shootouts, villainous doctors, and even pandemics of the past. Come learn a little more about Bloody Berlin….if you dare!Kick start your spooky season with us on Friday the 13th in September! There's no better time to learn about bloody Berlin than on the unluckiest day of the year!Admission:\$31 per person plus HST. Advance ticket purchase is required for this event, there will be no tickets sold at the door. Membership discount applies. No refunds.Information about Event:Suitable for ages 16 and up.Event runs rain or shine. This event takes place entirely outdoors and there will be no access to washrooms. The Historic Haus and galleries will be closed.Participants should dress for the weather and bring a flashlight (if possible).Please not
}
\vspace{10px}

\subtitle{Chilling Candlelit Evenings}

\articlecontent{

\qrcode[height=1.5cm]{https://calendar.waterlooregionmuseum.ca/Default/Detail/2024-10-19-1900-Chilling-Candlelit-Evenings}
\vspace{10px}

Our Chilling Candlelit Evenings are sure to give you a thrill! Visitors will get to experience Schneider Haus in a whole new light, at night! Guests will have the opportunity to tour through what some claim as the most haunted house in Kitchener and decide whether the ghost stories are true! You can expect to hear about chilling historic events that took place in the town of Berlin, funeral practices, charming, as well as some stories from visitors who claim to have had supernatural experiences.On October 19th and 25th! Connect with local spiritual medium Angelina who runs The Angelic Alchemist! Angelina will be doing one card tarot pulls for guests during our evening tour! Afterwards shop through some of her gorgeous products! Hear from Paranormal Investigator and Social Media star Hauntingly Krista around her experiences of investigating Schneider Haus!Are you brave enough to creep through Schneider Haus at night? Visits are scheduled for up to 60 minutes, the last tickets of the eve
}
\vspace{10px}

\headline{October 20, 2024}

\subtitle{Fibreworks 20th Anniversary Collection Show}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806618}
\vspace{10px}

September 7 - December 1, 2024In celebration of the 20th anniversary, see a selection of works acquired from past Fibreworks.Explore Fibreworks 20th Anniversary Collection Show.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Cambridge Art Galleries |Adults |EVENT TYPE: |Exhibitions + Openings |TAGS: |Culture Days |
}
\vspace{10px}

\subtitle{Stitching Science}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806764}
\vspace{10px}

September 30 - December 15, 2024Cambridge Art Galleries' inaugural pop-up exhibition at Idea Exchange, Old Post Office, features the work of Guelph-based artist Lauren Wright Vartanian. Her latest work, Stitching Science, merges art and science in 27 intricate diagrammatic embroideries. A culmination of three years of work and countless stitches, these embroideries, each representing a letter of the alphabet, depict scientific concepts in a creative and accessible way. This exhibition coincides with Wright Vartanian’s book release, Stitching Science: Exploring Science from A to Z, published by Firefly Books in the fall of 2024.Lauren Wright Vartanian is a multidisciplinary artist currently focusing on textile art. She has a Bachelor of Fine Arts in Drawing and Painting from OCAD University, where she graduated in 2006. She has been creating and selling art under the name Neurons and Nebulas since 2016. Her work blends art and science in a way that is fun and educational, but also beaut
}
\vspace{10px}

\subtitle{Stock-in-Transit}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11806980}
\vspace{10px}

September 12, 2024 - January 17, 2025Visit the lobby at Idea Exchange Queen's Square to experience an installation featuring a vibrant collection of items draping the doorway. The installation encourages a moment of pause to wonder and search as the work inspires critiques of consumerism. Torres’ installation uses familiar domestic, institutional, and recreational items to elevate our appreciation of the everyday while also inviting reflection on the challenges of consumer culture—our tendency to accumulate and the growing complexities of storing, recycling, and disposing of surplus goods.This installation reuses the items from Material Culture, an exhibition produced by the University of Waterloo Art Gallery. They generously allowed us to give the items another life before donating them to consumer distribution.Explore: José Luis Torres: A Site-Specific InstallationAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your
}
\vspace{10px}

\subtitle{Next in Fibre: 20th Anniversary of Fibreworks}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11807117}
\vspace{10px}

August 24 - November 10, 2024This latest iteration of our fibre-based group exhibition Next In Fibre: 20th Anniversary of Fibreworks combines the strengths of Cambridge Art Galleries’ two biannual exhibitions: Fibreworks and SHOW (the emerging artist exhibition) to present works by emerging artists working with fibre as a medium.Artists exhibiting in Next In Fibre: 20th Anniversary of Fibreworks include: Michèle Guevara, Julie Hall, Danielle Harris, Alexia-Leana Kokozaki, Vanessa Krause, Alyssa Kusik, Roda Medhat, Amber Helene Muller St. Thomas, Olivia Mae Sinclair, and Justin Ming Yong.Explore Next In Fibre: 20th Anniversary of FibreworksAccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered progra
}
\vspace{10px}

\subtitle{Halloween Crafternoon}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11644913}
\vspace{10px}

Create some spooky crafts using the equipment in the Makerspace.Uncover some ghoulish crafts using the laser cutter and Cricut machines. You’re in for a treat, not a trick, as you make projects to celebrate the fall season.Children may attend with an adult.AccessibilityIf you require an accessibility accommodation for this program or event, please tell us how we can meet your needs as soon as possible so arrangements can be organized. If you require a sign language interpreter, please let us know at least two-weeks (10 working weekdays) before the program date.   If you are attending a registered program with a support person, please add your support worker as a guest when you sign up.COST: FreeAGE GROUP: |Teens |Adults |EVENT TYPE: |Maker Programs |TAGS: |Crafts |Crafting |Arts |
}
\vspace{10px}

\subtitle{Life's a Story}

\articlecontent{

\qrcode[height=1.5cm]{https://ideaexchange.libnet.info/event/11815550}
\vspace{10px}

Learn about the lives of people in your community with small group conversations.Each persons journey is a book and at this unique program, you will have the opportunity to listen to personal journeys and converse with three live books from our community. Participate in three small group interactions to expand your knowledge and build understanding with various members of our community.Come Alive - How to self publish and promote your book, by Paul LanganPaul Langan is a Canadian author, historian, community sports volunteer, and founder of the High Speed Rail Canada. Paul has written over 29 booklets, short stories, and books, including, Hespeler's Hidden Secrets, The Three Hotels of Preston, and his latest work, Classic Hockey Stories from Pulps Golden Era. Paul has spent most of his adult life in youth sports organizations. He coached and was convenor for Hespeler Minor Hockey, was a coach for Cambridge Youth Soccer, and the founder and President of Scorpions Youth Volleyball Club.F
}
\vspace{10px}
\end{multicols}
\end{document}